---
title: Technology mediation in child sexual exploitation and abuse in Africa and Asia
authors: Ghai et al.
subtitle: Modelling script (complete case analysis)
format: 
  typst:
    toc: true
    toc-depth: 2
  pdf:
    toc: true
    toc-depth: 2
    echo: false
    number_sections: true
    fig_caption: true
    fig_height: 12
    fig_width: 8
    latex_engine: xelatex
    fontsize: 10pt
    mainfont: "Times New Roman"
    header-includes:
      - \usepackage{pdflscape}   
      - \usepackage{geometry}     
      - \geometry{margin=1in}     
      - \usepackage{longtable} 
      - \usepackage{adjustbox}  
  html:
    toc: true
    toc-depth: 2
    self-contained: true
    number_sections: true
    fig_caption: true
    highlight-style: pygments
    css: styles.css
---

# Analysis Overview

To examine associations between demographic and socio-cultural factors and disclosure of technology-facilitated CSEA, we fit Bayesian multilevel logistic regression models using brms with survey weights. All analyses used complete-case with missing data. 

**Model Specifications**

1. **Pre-registered confirmatory analysis**: Logistic regression with all predictors (gender, age, premarital sex attitudes, gender norms, enabling parental  mediation, sex education, help-seeking, digital skills), using survey weights but no random effects.

2. **Pre-registered exploratory analysis**: Multilevel models with random intercepts by country (n=12), examining three disclosure outcomes:
   - Any disclosure (toldall): disclosure to any channel
   - Formal disclosure (toldformal): to police, helpline, teacher, or social worker
   - Informal disclosure (toldinformal): to family or friends or other adults

3. **Channel-specific models** (exploratory, not pre-registered): Separate multilevel models for each of ten disclosure channels, using identical predictors and random intercepts by country. This approach examines whether predictors vary by disclosure channels.

4. **Random slopes sensitivity analysis** (exploratory, not pre-registered): For each predictor, we fit a model with both random intercepts and random slopes, allowing predictor effects to vary by country. Models were compared using leave-one-out cross-validation (LOO-CV) with Pareto-smoothed importance sampling.

All models used Bernoulli family with logit link. We ran 4 chains with 2,000 iterations (1,000 warmup) using cmdstanr backend with adapt_delta=0.99. We assessed model fit using LOO-CV and Pareto-k diagnostics. For channel-specific models, we calculated events per variable (EPV) to assess statistical power.
```{r}
#| label: options
#| message: false
#| cache: false

# Load packages
library(tidyverse)
library(brms)
library(posterior)
library(bayesplot)
library(bayestestR)
library(tidybayes)
library(marginaleffects)
library(loo)
library(patchwork)
library(survey)
library(srvyr)
library(knitr)
library(kableExtra)
library(gt)
library(gtsummary)
library(scales)
library(viridis)
library(colorspace)
library(RColorBrewer)
library(corrplot)
library(ggrepel)
library(ggdist)
library(ggh4x)
library(ggnewscale)
library(car)
library(performance)
library(broom.mixed)
library(mice)
library(janitor)
library(glue)
library(rlang)
library(rstan)

knitr::opts_chunk$set(dev = "png")

# Modelling: Always run brms with cmdstanr maybe with threading
dir.create("models", FALSE)
options(
  brms.backend = "cmdstanr",
  mc.cores = min(parallel::detectCores(), 8),
  brms.threads = parallel::detectCores() %/% 4
)

# Make plots pretty 
theme_set(
  theme_linedraw() +
    theme(panel.grid = element_blank())
)

# Output options
opts_chunk$set(
  eval = TRUE,
  cache = TRUE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  echo = knitr::is_html_output()
)
options(digits = 2)
ITER <- 2000
```

```{r, echo=FALSE}
#| label: load-data-victim
d_victim <- readRDS("data-raw/victim_dh.rds")
```

```{r select-vars}
#| label: select-variables
d_victim <- d_victim %>%
  select(
    pid = CBU_ID, 
    sex, 
    age, 
    presex, 
    nindex, 
    parentmediate,
    sexed,
    urbanrural, 
    helpseeking, 
    digitalskills, 
    COUNTRY, 
    wgt_scaled, 
    victim,
    starts_with("toldnoone_"), 
    starts_with("abuse_"), 
    starts_with("police_"),
    starts_with("helpline_"), 
    starts_with("teacher_"), 
    starts_with("sworker_"),
    starts_with("friend_"), 
    starts_with("sibling_"), 
    starts_with("father_"),
    starts_with("mother_"), 
    starts_with("other_"), 
    starts_with("othera_")
  )

# Identical to function in 2a_disclosure.qmd
# d_report <- disclosure_data(d_victim)
```

```{r disclosure-wrangling}
#| include: false 
#| message: false
#| echo: false

# Duplicated here so this script runs independently
disclosure_data <- function(data) {
  
  # filter victims only
  victims <- data %>% filter(victim == 1)
  
  # disclosure channel names
  channels <- c("toldnoone", "police", "helpline", "teacher", "sworker", 
                "friend", "sibling", "father", "mother", "other", "othera")
  
  # function to check if disclosed any abuse type to this channel
  check_channel <- function(prefix, data) {
    # abuse types are a-i
    cols <- paste0(prefix, "_", letters[1:9])
    rowSums(data[cols], na.rm = TRUE) > 0
  }
  
  # apply to each channel
  for (ch in channels) {
    victims[[ch]] <- check_channel(ch, victims)
  }
  
  ## create disclosure categories
  victims %>%
    mutate(
      # any disclosure?
      toldall = police | helpline | teacher | sworker | friend | 
                 sibling | father | mother | other | othera,
      # formal vs informal
      toldformal = police | helpline | teacher | sworker,
      toldinformal = friend | sibling | father | mother | other | othera,
      
      # make mutually exclusive 
      no_disclosure = !toldall,
      informal_only = toldinformal & !toldformal,
      formal_only = toldformal & !toldinformal,
      both_channels = toldinformal & toldformal,
      
      # now factor
      disclosure_type = case_when(
        both_channels ~ "Both",
        informal_only ~ "Informal only",
        formal_only ~ "Formal only",
        no_disclosure ~ "None"
      ),
      disclosure_type = factor(disclosure_type, 
                              levels = c("None", "Informal only", "Formal only", "Both"))
    )
}

d_report <- disclosure_data(d_victim)
```


## Define Labels
```{r}
# labels
channel_labels <- c(
  police   = "Police",
  helpline = "Helpline",
  sworker  = "Social Worker",
  teacher  = "Teacher",
  mother   = "Mother",
  father   = "Father",
  sibling  = "Sibling",
  friend   = "Friend",
  other    = "Other",
  othera   = "Other Adult"
)

# facet labels for predictors including variations (used throughout)
facet_labels <- c(
  "b_Intercept" = "Intercept",
  "b_sex1" = "Girl (vs Boy)",
  "b_sexGirl" = "Girl (vs Boy)",
  "sex1" = "Girl (vs Boy)",
  "sexGirl" = "Girl (vs Boy)",
  "b_age" = "Age (per year)",
  "age" = "Age (per year)",
  "b_presex1" = "Premarital sex",
  "presex1" = "Premarital sex",
  "b_nindex" = "Inequitable gender attitudes",
  "nindex" = "Inequitable gender attitudes",
  "b_parentmediate" = "Enabling parental mediation",
  "parentmediate" = "Enabling parental mediation",
  "b_sexed1" = "Sex education",
  "sexed1" = "Sex education",
  "b_helpseeking1" = "Help-seeking",
  "helpseeking1" = "Help-seeking",
  "b_digitalskills" = "Digital skills",
  "digitalskills" = "Digital skills"
)

# separate label map for odds-ratio plots - some intentional redundancy 
predictor_map <- c(
  b_Intercept     = "Intercept",
  b_sex1          = "Girls (vs Boys)",
  b_age           = "Age (per year)",
  b_presex1       = "Premarital sex",
  b_nindex        = "Inequitable attitudes towards sex",
  b_parentmediate = "Enabling parental mediation",
  b_sexed1        = "Sex education",
  b_helpseeking1  = "Help-seeking",
  b_digitalskills = "Digital skills to report"
)
predictors_set <- names(predictor_map)

# clean labels for correlation plots
clean_labels <- c(
  "sex1" = "Girl (vs Boy)",
  "sexGirl" = "Girl (vs Boy)",
  "age" = "Age (per year)",
  "presex1" = "Premarital sex",
  "nindex" = "Inequitable gender attitudes",
  "parentmediate" = "Enabling parental mediation",
  "sexed1" = "Sex education",
  "helpseeking1" = "Help-seeking",
  "digitalskills" = "Digital skills"
)
```

Select relevant variables
```{r}

d_report <- d_report %>%
       select(
      c(
    -ends_with(c(
      "_a", 
      "_b", 
      "_c", 
      "_d", 
      "_e", 
      "_f", 
      "_g", 
      "_h", 
      "_i")),
      victim
    )
  )
```

## (1) Pre-Registered Confirmatory Analysis: Logistic Regression (With Missing)
This model estimates the association between predictors and the likelihood of disclosure (toldall), using logistic regression and incorporating survey weights. This analysis includes the model fit performed on the data with missing values.

```{r}
#| output: false
fit_report_all_glm <- brm(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + 
    digitalskills,
  data = d_report,
  family = bernoulli(),
  control = list(adapt_delta = 0.99),
  file = "models/brm-report-all-glm"
)
```

We extract posterior summaries and compute odds ratios with 95% credible intervals. Labels are applied for interpretability.
```{r}
posterior_results <- posterior_summary(fit_report_all_glm)

posterior_df <- as.data.frame(posterior_results) %>%
  tibble::rownames_to_column(var = "Parameter") %>%
  setNames(c("Parameter", "Estimate", "Est.Error", "Lower_CI", "Upper_CI")) %>%
  filter(Parameter != "b_Intercept") %>%
  mutate(
    Parameter = case_when(
      Parameter %in% names(facet_labels) ~ facet_labels[Parameter],
      sub("^b_", "", Parameter) %in% names(facet_labels) ~ facet_labels[sub("^b_", "", Parameter)],
      TRUE ~ Parameter
    ),
    `Odds Ratio` = exp(Estimate),
    `Lower OR CI` = exp(Lower_CI),
    `Upper OR CI` = exp(Upper_CI)
  ) %>%
  select(Parameter, Estimate, Lower_CI, Upper_CI, `Odds Ratio`, `Lower OR CI`, `Upper OR CI`)

posterior_df %>%
  knitr::kable(
    digits = 3,
    col.names = c("Parameter", "Estimate", "Lower CI", "Upper CI", 
                  "Odds Ratio", "Lower OR CI", "Upper OR CI"),
    booktabs = TRUE,
    align = c("l", rep("r", 6))
  ) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
```

## (2) Pre-Registered Exploratory Analysis: Random Intercepts Model (With Missing)
As part of our pre-registered exploratory analyses, we fit three models examining disclosure across three categories:
- toldall (any disclosure),
- toldformal (formal channels only),
- toldinformal (informal channels only).
```{r}
#| label: fit-report-separate
#| output: false

# common formula stem
model_stem <- "| weights(wgt_scaled) ~ sex + age + presex + nindex + parentmediate + sexed + helpseeking + digitalskills + (1 | COUNTRY)"

# composite disclosure outcomes
model_toldall       <- paste("toldall", model_stem)
model_toldformal    <- paste("toldformal", model_stem)
model_toldinformal  <- paste("toldinformal", model_stem)
```

All models include random intercepts by country and use scaled weights.
```{r}
# any disclosure
fit_report_all <- brm(
  model_toldall,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-all",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)

# formal disclosure
fit_report_formal <- brm(
  model_toldformal,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-formal",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)

# informal disclosure
fit_report_informal <- brm(
  model_toldinformal,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-informal",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)
```

## (3) Channel-specific models (exploratory, not pre-registered)
We also fit channel-specific models which fit separate logistic regression models for each channel using identical predictor sets, allowing us to: (a) identify channel-specific predictors without aggregation, (b) examine which factors distinguish disclosure to one particular channel versus non-disclosure to that channel, and (c) provide granular insight into the distinct pathway’s children use when disclosing. 

```{r}
#| label: fit-report-diff
#| output: false

# formal channels
model_police        <- paste("police", model_stem)
model_helpline      <- paste("helpline", model_stem)
model_sworker       <- paste("sworker", model_stem)
model_teacher       <- paste("teacher", model_stem)

# informal channels - family
model_mother        <- paste("mother", model_stem)
model_father        <- paste("father", model_stem)
model_sibling       <- paste("sibling", model_stem)

# informal channels - peers
model_friend        <- paste("friend", model_stem)

# other
model_other         <- paste("other", model_stem)
model_othera        <- paste("othera", model_stem)
```
Now we fit all models 
```{r}
# police
fit_report_police <- brm(
  model_police,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-policee",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)

# helpline
fit_report_helpline <- brm(
  model_helpline,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-helpline",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)

# social worker
fit_report_sworker <- brm(
  model_sworker,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-sworker",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)

# teacher
fit_report_teacher <- brm(
  model_teacher,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-teacher",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)

# mother
fit_report_mother <- brm(
  model_mother,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-mother",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)

# father
fit_report_father <- brm(
  model_father,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-father",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)

# sibling
fit_report_sibling <- brm(
  model_sibling,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-sibling",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)

# friend
fit_report_friend <- brm(
  model_friend,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-friend",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)

# other adults
fit_report_othera <- brm(
  model_othera,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  file = "models/brm-report-othera",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)
```
We create named list of all models and set up a function to extract posterior summaries from all tables 
```{r}
# all models 
all_models <- list(
  toldall = fit_report_all,
  toldformal = fit_report_formal,
  toldinformal = fit_report_informal,
  police = fit_report_police,
  helpline = fit_report_helpline,
  sworker = fit_report_sworker,
  teacher = fit_report_teacher,
  mother = fit_report_mother,
  father = fit_report_father,
  sibling = fit_report_sibling,
  friend = fit_report_friend,
  othera = fit_report_othera
)

report_names <- c(
  "toldall" = "Any Disclosure",
  "toldformal" = "Formal Disclosure",
  "toldinformal" = "Informal Disclosure",
   "police"   = "Police",
  "helpline" = "Helpline",
  "sworker"  = "Social Worker",
  "teacher"  = "Teacher",
  "mother"   = "Mother",
  "father"   = "Father",
  "sibling"  = "Sibling",
  "friend"   = "Friend",
  "othera"   = "Other Adult"
)
# summarize all 
summarise_draws_pop <- function(model_list, facet_labels, report_names) {
  names_list <- names(model_list)
  
  model_list %>%
    map(~ {
      ps <- posterior::summarise_draws(
        as_draws_df(.x),
        .cores = 1
      ) %>%
        filter(grepl("^b_", variable))
      ps
    }) %>%
    bind_rows(.id = "report") %>%
    mutate(
      report = factor(report, levels = names_list, labels = report_names[names_list]),
      term = as.character(variable)
    ) %>%
    filter(term != "b_Intercept") %>%
    mutate(
      predictor = case_when(
        term %in% names(facet_labels) ~ facet_labels[term],
        sub("^b_", "", term) %in% names(facet_labels) ~ facet_labels[sub("^b_", "", term)],
        TRUE ~ term
      ),
      Estimate = glue::glue(
  "{scales::number(mean, accuracy = 0.01)} ",
  "[{scales::number(q2.5, accuracy = 0.01)}, ",
  "{scales::number(q97.5, accuracy = 0.01)}]"
      )
    ) %>%
    select(predictor, report, Estimate) %>%
    pivot_wider(names_from = report, values_from = Estimate)
}
```

### Model summary: Random Intercepts Model
```{r}
#| label: tbl-composite-channels
#| tbl-cap: "Composite disclosure outcomes (posterior means with 95% credible intervals)"

list(
  fit_report_all,
  fit_report_formal,
  fit_report_informal
) %>%
  purrr::map(~ summarise_draws_pop(.x)) %>%
  bind_rows(.id = "report") %>%
  mutate(
    report    = factor(report, levels = 1:3, labels = c("All", "Formal", "Informal")),
    variable  = as.character(variable),
    predictor = coalesce(unname(facet_labels[variable]), variable),
    Estimate  = glue("{number(Estimate, accuracy = .01)} [{number(Q2.5, accuracy = .01)}, {number(Q97.5, accuracy = .01)}]")
  ) %>%
  select(predictor, report, Estimate) %>%
  pivot_wider(names_from = report, values_from = Estimate) %>%
  kable()
```

### Variance Inflation Factor
All predictors entered as 1-df terms. We computed classic VIFs (and the corresponding standard-error inflation, √VIF) on the complete-case analytic matrix for each outcome (samples differ by missingness). All VIFs were 1.0–2.0, well below common thresholds used to flag multicollinearity (e.g., VIF ≥5–10), indicating no substantial collinearity.
```{r} 
outcomes   <- c("toldall","toldformal","toldinformal")
predictors <- c("sex","age","presex","nindex","parentmediate","sexed","helpseeking","digitalskills")

vif <- function(m) {
  v <- car::vif(m)
  tibble(
    term   = names(v),
    VIF    = as.numeric(v),
    `√VIF` = sqrt(as.numeric(v))
  )
}

dat_cc <- d_report %>%
  select(all_of(c(outcomes, predictors, "wgt_scaled"))) %>%
  drop_na()

vif_table <- map_dfr(outcomes, function(y){
  fml <- reformulate(predictors, response = y)
  m <- glm(fml, data = dat_cc, family = binomial(), weights = wgt_scaled)
  vif(m) %>% mutate(outcome = y, .before = 2)
}) %>%
  arrange(outcome, desc(`√VIF`)) %>%
  mutate(
    VIF    = sprintf("%.2f", VIF),
    `√VIF` = sprintf("%.2f", `√VIF`),
    outcome = dplyr::recode(outcome,
      toldall      = "Any channels",
      toldformal   = "Formal channels",
      toldinformal = "Informal channels"
    ),
    term = dplyr::recode(term,
      sex           = "Girls (vs Boys)",
      age           = "Age (per year)",
      presex        = "Premarital sex",
      nindex        = "Inequitable gender attitudes",
      parentmediate = "Enabling parental mediation",
      sexed         = "Sex education",
      helpseeking   = "Help-seeking",
      digitalskills = "Digital skills to report"
    )
  )

kable(
  vif_table %>% select(outcome, term, VIF, `√VIF`),
  booktabs    = TRUE,
  longtable   = TRUE,
  col.names   = c("Outcome", "Term", "VIF", "√VIF"),
  digits      = NA,
  format.args = list(scientific = FALSE)
) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))
```

### Computing R2 
We also summarise model fit using Bayesian R² (posterior mean, 95% CI) and, for mixed models abd Nakagawa’s marginal/conditional R²
```{r} 
fits <- list(
  toldall      = fit_report_all,       
  toldformal   = fit_report_formal,    
  toldinformal = fit_report_informal   
)

# summarize Bayesian R2 
bayes_R2_summary <- function(fit, probs = c(.025, .5, .975), seed = 123) {
  set.seed(seed) 
  r2_draws <- bayes_R2(fit)
  tibble(
    bayes_R2_mean = mean(r2_draws),
    bayes_R2_med  = median(r2_draws),
    bayes_R2_ll   = quantile(r2_draws, probs[1]),
    bayes_R2_ul   = quantile(r2_draws, probs[3])
  )
}

r2 <- map_dfr(names(fits), function(nm){
  f <- fits[[nm]]
  nak <- performance::r2_nakagawa(f) 
  bay <- bayes_R2_summary(f)            
  tibble(
    outcome         = nm,
    bayes_R2_mean   = bay$bayes_R2_mean,
    bayes_R2_ll     = bay$bayes_R2_ll,
    bayes_R2_ul     = bay$bayes_R2_ul,
    r2_marginal     = nak$R2_marginal,
    r2_conditional  = nak$R2_conditional
  )
}) %>%
  mutate(
    across(where(is.numeric), ~ round(., 3)),
    outcome = dplyr::recode(outcome,
      toldall      = "Any channels",
      toldformal   = "Formal channels",
      toldinformal = "Informal channels"
    )
  )

kable(r2, digits = 3, 
      booktabs = TRUE,
      col.names = c("Outcome", "Bayesian R²", "Lower", "Upper", 
                     "Marginal R²", "Conditional R²")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))
```

```{r}
#| label: tbl-formal-channels
#| tbl-cap: "Formal disclosure channels (posterior means with 95% credible intervals)"

formal_models <- list(
  police = fit_report_police,
  helpline = fit_report_helpline,
  sworker = fit_report_sworker,
  teacher = fit_report_teacher
)

summarise_draws_pop(formal_models, facet_labels, report_names) %>%
  kable(booktabs = TRUE, align = c("l", rep("r", 4))) %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
```
 
```{r}
#| label: tbl-family-channels
#| tbl-cap: "Informal disclosure channels (posterior means with 95% credible intervals)"

informal_models <- list(
  mother = fit_report_mother,
  father = fit_report_father,
  sibling = fit_report_sibling,
  friend = fit_report_friend,
  othera = fit_report_othera
)

summarise_draws_pop(informal_models, facet_labels, report_names) %>%
  kable(booktabs = TRUE, align = c("l", rep("r", 3))) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
```

### Events-per-variable (EPV) (channel specific)
We first evaluated statistical power for each channel using events-per-variable (EPV) criteria. We excluded one channel (other: n=19, 0.9%, EPV = 2.1) from regression analysis due to insufficient events. Three formal channels (police: n = 59, helpline: n = 63, social worker: n = 58; EPV = 6.4 to 7.0) have limited power and should be interpreted as exploratory findings. All other channels met conventional power thresholds (EPV>10).

```{r}
#| label: tbl-epv
#| tbl-cap: Channel-specific sample sizes and events per variable (EPV)

# channels used in EPV table 
channels <- intersect(names(d_report), names(channel_labels))

# build epv table
epv_balance <- d_report %>%
  select(any_of(channels)) %>%
  mutate(across(everything(), ~ suppressWarnings(as.logical(.)))) %>%
  summarise(
    across(
      everything(),
      list(
        yes = ~ sum(. == TRUE,  na.rm = TRUE),
        no  = ~ sum(. == FALSE, na.rm = TRUE)
      ),
      .names = "{.col}.{.fn}"
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to  = c("channel", ".value"),
    names_sep = "\\."
  ) %>%
  rename(
    n_yes = yes,
    n_no  = no
  ) %>%
  mutate(
    n_total        = n_yes + n_no,
    prop_yes       = ifelse(n_total > 0, n_yes / n_total, NA_real_),
    `Prevalence (%)` = round(100 * prop_yes, 1),
    EPV            = round(n_yes / 9, 1),  # 9 predictors
    sufficient     = n_yes >= 30 & prop_yes >= 0.01,
    status = case_when(
      n_yes < 10      ~ "Very sparse (<10 events)",
      n_yes < 30      ~ "Sparse (10–30 events)",
      prop_yes < 0.01 ~ "Rare (<1%)",
      TRUE            ~ "Adequate"
    ),
    analysis_type = case_when(
      !sufficient ~ "Descriptive only",
      n_yes < 100 ~ "Regression (exploratory)",
      TRUE        ~ "Regression"
    )
  ) %>%
  arrange(desc(prop_yes))

exclude_channels <- epv_balance %>%
  filter(!sufficient) %>%
  pull(channel)
```

```{r}

epv_balance %>%
  transmute(
    Channel       = dplyr::recode(channel, !!!channel_labels),
    `N disclosed` = n_yes,
    `N total`     = n_total,
    `Prevalence (%)`,
    EPV,
    status,
    Analysis      = analysis_type
  ) %>%
  knitr::kable(
    caption = "Disclosure balance by channel"
  )
```
Now we compute odds ratios for each channel
```{r}
or_results <- {
  rl <- lapply(names(all_models), function(ch) {
    fit <- all_models[[ch]]
    posterior_summary(fit, variable = predictors_set) %>%
      as.data.frame() %>%
      tibble::rownames_to_column("parameter") %>%
      mutate(channel = ch)
  })
  bind_rows(rl) %>%
    mutate(
      Predictors = dplyr::recode(parameter, !!!predictor_map),
      OR     = exp(Estimate),
      OR_lwr = exp(Q2.5),
      OR_upr = exp(Q97.5),
      sig    = (Q2.5 > 0 & Q97.5 > 0) | (Q2.5 < 0 & Q97.5 < 0),
      cell   = dplyr::case_when(
        !sig ~ sprintf("%.2f (%.2f–%.2f)", OR, OR_lwr, OR_upr),
        OR >= 1.5 | OR <= 0.67 ~ sprintf("**%.2f (%.2f–%.2f)†**", OR, OR_lwr, OR_upr),
        TRUE ~ sprintf("**%.2f (%.2f–%.2f)**", OR, OR_lwr, OR_upr)
      )
    )
}

# Wide table
coef_table <- or_results  %>%
  select(channel, Predictors, cell) %>%
  pivot_wider(names_from = channel, values_from = cell) %>%
  rename_with(~ ifelse(.x %in% names(channel_labels), channel_labels[.x], .x), everything())
```

## Forest plot
```{r}
#| label: fig-forest-prep
#| fig-width: 12
#| fig-height: 10

# data for forest plot
forest_df <- or_results %>%
  filter(Predictors != "Intercept") %>%
  left_join(
    epv_balance %>% select(channel, n_yes, EPV), 
    by = "channel"
  ) %>%
  mutate(
    exploratory = n_yes < 100,
    channel_group = case_when(
      channel %in% c("toldall", "toldformal", "toldinformal") ~ "1_Composite",
      channel %in% c("police", "helpline", "sworker", "teacher") ~ "2_Formal",
      channel %in% c("mother", "father", "sibling") ~ "3_Family",
      channel == "friend" ~ "4_Peer",
      TRUE ~ "5_Other"
    ),
    channel_label = case_when(
      channel == "toldall" ~ "Any channel",
      channel == "toldformal" ~ "Formal (composite)",
      channel == "toldinformal" ~ "Informal (composite)",
      channel %in% names(channel_labels) ~ channel_labels[channel],
      TRUE ~ channel
    ),
    Predictors = factor(
      Predictors, 
      levels = c(
        "Girls (vs Boys)",
        "Age (per year)",
        "Premarital sex",
        "Inequitable attitudes towards sex",
        "Enabling parental mediation",
        "Sex education",
        "Help-seeking",
        "Digital skills to report"
      )
    )
  ) %>%
  group_by(Predictors) %>%
  mutate(channel_label = fct_reorder(channel_label, OR, .desc = FALSE)) %>%
  ungroup()
```

```{r}
#| label: fig-forest-channels
#| fig-cap: "Predictors of disclosure across channels (forest plot)"
#| fig-width: 12
#| fig-height: 10

# forest plot
forest_plot <- ggplot(forest_df, aes(x = OR, y = channel_label)) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey40", linewidth = 0.4) +
  geom_errorbarh(
    aes(xmin = OR_lwr, xmax = OR_upr, color = sig, alpha = exploratory),
    height = 0.3, 
    linewidth = 0.6
  ) +
  geom_point(aes(color = sig, alpha = exploratory), size = 2.5) +
  facet_wrap(~ Predictors, scales = "free_x", ncol = 3) +
  scale_color_manual(
    values = c(`TRUE` = "#E74C3C", `FALSE` = "grey60"),
    labels = c(`TRUE` = "95% CI excludes 1", `FALSE` = "95% CI includes 1"),
    name = NULL
  ) +
  scale_alpha_manual(
    values = c(`TRUE` = 0.6, `FALSE` = 1.0),
    breaks = c(TRUE, FALSE),
    labels = c(`TRUE` = "Exploratory (n<100)", `FALSE` = "Adequate power"),
    na.value = 1.0, 
    name = NULL
  ) +
  scale_x_continuous(
    trans = "log10", 
    breaks = c(0.5, 0.75, 1, 1.5, 2, 3, 4),
    labels = c("0.5", "0.75", "1.0", "1.5", "2.0", "3.0", "4.0")
  ) +
  labs(
    x = "Odds Ratio (log scale)", 
    y = NULL,
    title = "Predictors of Disclosure Across Channels"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    legend.position = "bottom",
    legend.box = "vertical",
    legend.key.width = unit(1.5, "cm"),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.border = element_rect(fill = NA, color = "grey80", linewidth = 0.3),
    strip.text = element_text(face = "bold", size = 10),
    strip.background = element_rect(fill = "grey95", color = NA),
    axis.text.y = element_text(size = 9),
    axis.text.x = element_text(size = 8),
    plot.title = element_text(face = "bold", size = 13, hjust = 0.5),
    plot.margin = margin(10, 10, 10, 10)
  )

forest_plot

ggsave(
  "forest_channels.png", 
  forest_plot,
  width = 12, 
  height = 10, 
  dpi = 300,
  bg = "white"
)
```

## Combined Table (All Channels Odds Ratios)

```{r}
#| label: tbl-all-channels
#| tbl-cap: "Predictors of disclosure across all channels (odds ratios with 95% CIs)"

coef_table_all <- or_results %>%
  mutate(
    channel_clean = case_when(
      channel == "toldall"      ~ "Any",
      channel == "toldformal"   ~ "Formal",
      channel == "toldinformal" ~ "Informal",
      channel %in% names(channel_labels) ~ channel_labels[channel],
      TRUE ~ channel
    )
  ) %>%
  select(channel_clean, Predictors, cell) %>%
  pivot_wider(
    names_from  = channel_clean,
    values_from = cell
  ) %>%
  select(
    Predictors,
    Any, Formal, Informal,                      # composite
    Police, Helpline, `Social Worker`, Teacher, # formal channels
    Mother, Father, Sibling, Friend, `Other Adult` # informal channels
  )

kable(
  coef_table_all,
  booktabs = TRUE,
  escape   = FALSE,
  align    = c("l", rep("r", 12))
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    font_size     = 6,
    full_width    = TRUE
  ) %>%
  add_header_above(
    c(" " = 1, "Composite" = 3, "Formal" = 4, "Informal" = 5)
  ) %>%
  footnote(
    general = c(
      "**Bold** indicates 95% CI excludes 1.0; † indicates substantive effect (OR ≥ 1.5 or ≤ 0.67)",
      "Police, Helpline, and Social Worker have limited sample sizes (EPV < 10)."
    ),
    general_title      = "Note:",
    footnote_as_chunk  = TRUE
  )
```

## Correlations between predictors 
```{r} 
# plot weighted correlations for predictors
predictor_corr <- function(data, rhs, w = NULL,
                           tl_cex = 0.9, num_cex = 0.95, digits = 2,
                           clean_labels = NULL) {
  
  X <- model.matrix(as.formula(rhs), data = data)[, -1, drop = FALSE]
  X <- X[, apply(X, 2, function(z) sd(z, na.rm = TRUE) > 0), drop = FALSE]
  
  # rename columns again
  if (!is.null(clean_labels)) {
    for (nm in names(clean_labels)) {
      if (nm %in% colnames(X)) {
        colnames(X)[colnames(X) == nm] <- clean_labels[[nm]]
      }
    }
  }
  
  w <- if (is.null(w)) rep(1, nrow(X)) else w
  w <- ifelse(is.finite(w) & w > 0, w, 1)
  
  ok <- complete.cases(X)
  X  <- X[ok, , drop = FALSE]
  w  <- w[ok]
  
  Xs <- scale(X, center = TRUE, scale = TRUE)
  Xw <- sweep(Xs, 1, sqrt(w), `*`)
  M  <- cov2cor(crossprod(Xw) / sum(w))
  
  col_div <- colorRampPalette(c("#1b6ca8", "#f7f7f7", "#b22222"))(240)
  op <- par(mar = c(1.2, 1.2, 1.2, 1.2))
  on.exit(par(op), add = TRUE)
  
  corrplot(
    M,
    method        = "color",
    type          = "upper",
    tl.col        = "black",
    tl.cex        = tl_cex,
    tl.srt        = 45,
    cl.cex        = 0.9,
    cl.align      = "c",
    cl.ratio      = 0.15,
    col           = col_div,
    addgrid.col   = "white",
    number.cex    = num_cex,
    number.digits = digits,
    addCoef.col   = "black",
    diag          = FALSE,
    outline       = TRUE
  )
  
  invisible(M)
}
```

```{r}
# predictor correlations
rhs <- "~ sex + age + presex + nindex + parentmediate + sexed + helpseeking + digitalskills"
corr_preds <- predictor_corr(d_report, rhs, w = d_report$wgt_scaled, clean_labels = clean_labels)

# save 
png("figure_corr.pdf", 
    width = 6, 
    height = 4, 
    units = "in", 
    res = 300
    )

corr_preds <- predictor_corr(
  d_report, 
  rhs, 
  w = d_report$wgt_scaled, 
  clean_labels = clean_labels
)
dev.off()
```


## (4) Random slopes sensitivity analysis (exploratory, not pre-registered)
```{r}
# age
fit_report_all_age <- brm(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex +
    parentmediate + sexed + helpseeking + digitalskills +
    (1 + age | COUNTRY),
  data   = d_report,
  family = bernoulli(),
  backend = "cmdstanr",
  chains = 4,         
  cores  = 4,         
  iter   = 2000,     
  warmup = 1000,       
  threads = threading(2), 
  control = list(adapt_delta = 0.99),
  seed = 123,
  file = "models/brm-disclosure-all-age-cmd"
)

# gender
fit_report_all_sex <- brm(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex +
    parentmediate + sexed + helpseeking + digitalskills +
    (1 + sex | COUNTRY),
  data   = d_report,
  family = bernoulli(),
  backend = "cmdstanr",
  chains = 4,         
  cores  = 4,          
  iter   = 2000,       
  warmup = 1000,       
  threads = threading(2),  
  control = list(adapt_delta = 0.99),
  seed = 123,
  file = "models/brm-disclosure-all-sex-cmd"
)

# premartial sex
fit_report_all_presex <- brm(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex +
    parentmediate + sexed + helpseeking + digitalskills +
    (1 + presex | COUNTRY),
  data   = d_report,
  family = bernoulli(),
  backend = "cmdstanr",
  chains = 4,         
  cores  = 4,          
  iter   = 2000,       
  warmup = 1000,       
  threads = threading(2),  
  control = list(adapt_delta = 0.99),
  seed = 123,
  file = "models/brm-disclosure-all-presex-cmd"
)

# inequitable gender attitudes
fit_report_all_nindex <- brm(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex +
    parentmediate + sexed + helpseeking + digitalskills +
    (1 + nindex | COUNTRY),
  data   = d_report,
  family = bernoulli(),
  backend = "cmdstanr",
  chains = 4,          
  cores  = 4,          
  iter   = 2000,      
  warmup = 1000,       
  threads = threading(2),  
  control = list(adapt_delta = 0.99),
  seed = 123,
  file = "models/brm-disclosure-all-nindex -cmd"
)

# parentmediate
fit_report_all_parentmediate <- brm(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex +
    parentmediate + sexed + helpseeking + digitalskills +
    (1 +  parentmediate | COUNTRY),
  data   = d_report,
  family = bernoulli(),
  backend = "cmdstanr",
  chains = 4,         
  cores  = 4,         
  iter   = 2000,       
  warmup = 1000,      
  threads = threading(2), 
  control = list(adapt_delta = 0.99),
  seed = 123,
  file = "models/brm-disclosure-all-parentmediate-cmd"
)

# sex education
fit_report_all_sexed <- brm(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex +
    parentmediate + sexed + helpseeking + digitalskills +
    (1 + sexed | COUNTRY),
  data   = d_report,
  family = bernoulli(),
  backend = "cmdstanr",
  chains = 4,        
  cores  = 4,         
  iter   = 2000,      
  warmup = 1000,      
  threads = threading(2),  
  control = list(adapt_delta = 0.99),
  seed = 123,
  file = "models/brm-disclosure-all-sexed-cmd"
)

# helpseeking
fit_report_all_helpseeking <- brm(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex +
    parentmediate + sexed + helpseeking + digitalskills +
    (1 + helpseeking | COUNTRY),
  data   = d_report,
  family = bernoulli(),
  backend = "cmdstanr",
  chains = 4,          
  cores  = 4,         
  iter   = 2000,       
  warmup = 1000,       
  threads = threading(2),  
  control = list(adapt_delta = 0.99),
  seed = 123,
  file = "models/brm-disclosure-all-helpseeking-cmd"
)

# digital skills
fit_report_all_digitalskills <- brm(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex +
    parentmediate + sexed + helpseeking + digitalskills +
    (1 + digitalskills | COUNTRY),
  data   = d_report,
  family = bernoulli(),
  backend = "cmdstanr",
  chains = 4,          
  cores  = 4,         
  iter   = 2000,       
  warmup = 1000,      
  threads = threading(2),  
  control = list(adapt_delta = 0.99),
  seed = 123,
  file = "models/brm-disclosure-all-digitalskills-cmd"
)
```

### LOO disclosure models
Now we estimate a model's predictive accuracy from out-of-sample data using Pareto Smoothed Importance Sampling (PSIS-LOO)
```{r}
# loo 
loo_all_complete <-  loo(fit_report_all)
loo_age           <- loo(fit_report_all_age)
loo_sex           <- loo(fit_report_all_sex)
loo_presex        <- loo(fit_report_all_presex)
loo_nindex        <- loo(fit_report_all_nindex)
loo_parentmediate <- loo(fit_report_all_parentmediate)
loo_sexed         <- loo(fit_report_all_sexed)
loo_helpseeking   <- loo(fit_report_all_helpseeking)
loo_digitalskills <- loo(fit_report_all_digitalskills)

# loo compare 
loo_disclosuremodels <- loo::loo_compare(
  loo_all_complete,
  loo_age,
  loo_sex,
  loo_presex,
  loo_nindex,
  loo_parentmediate,
  loo_sexed,
  loo_helpseeking,
  loo_digitalskills
)

# relabel
loo_models <- list(
  "Full model (RI)"                        = loo_all_complete,
  "Age (random slope)"                     = loo_age,
  "Gender (random slope)"                  = loo_sex,
  "Premarital sex (random slope)"          = loo_presex,
  "Inequitable attitudes (random slope)"   = loo_nindex,
  "Parental mediation (random slope)"      = loo_parentmediate,
  "Sex education (random slope)"           = loo_sexed,
  "Help-seeking (random slope)"            = loo_helpseeking,
  "Digital skills (random slope)"          = loo_digitalskills
)
```

## Pareto-k summary for each model
We check PSIS-LOO diagnostics across several fitted models. The Pareto-k values flag whether the LOO approximation is reliable for each observation
```{r}
# pareto summary 
pk_summary <- function(x, label) {
  k <- pareto_k_values(x)
  
  data.frame(
    Model      = label,
    `max k`    = round(max(k), 2),
    `n > 0.7`  = sum(k > 0.7),
    check.names = FALSE
  )
}

paret_disclosure <- map_dfr(
  names(loo_models),
  ~ pk_summary(loo_models[[.x]], .x)
)

knitr::kable(
  paret_disclosure,
  caption = "PSIS-LOO Pareto-k diagnostics (k < 0.7 acceptable).",
  align   = "lrr"
)
```

## Plot LOO disclosure models
Finally, we plot ΔELPD with standard-error bars
```{r}

# loo comparison data
disclosurel_df <- as.data.frame(loo_disclosuremodels) %>%
  rownames_to_column("Model_raw") %>%
  transmute(
    Model_clean = str_replace_all(
      str_remove_all(Model_raw, "^loo\\(|\\)$"),
      "^x=",
      ""
    ),
    elpd_diff,
    se_diff
  )

#better labels
idx <- match(disclosurel_df$Model_clean, names(loo_models))
disclosurel_df$Model <- ifelse(
  is.na(idx),
  disclosurel_df$Model_clean,
  loo_models[idx]
)

# identify best model
best_model <- disclosurel_df %>%
  filter(elpd_diff == 0) %>%
  pull(Model)

# plot elpd with se bars
loo_disclosure <- ggplot(
  disclosurel_df,
  aes(x = reorder(Model, elpd_diff), y = elpd_diff)
) +
  geom_hline(
    yintercept = 0,
    linetype   = "dashed",
    color      = "grey60",
    linewidth  = 0.3
  ) +
  geom_errorbar(
    aes(ymin = elpd_diff - se_diff, ymax = elpd_diff + se_diff),
    width     = 0.2,
    linewidth = 0.5,
    color     = "grey40"
  ) +
  geom_point(
    size  = 4.5,
    shape = 21,
    fill  = "white",
    color = "white"
  ) +
  geom_point(
    aes(fill = Model == best_model),
    size  = 3.5,
    shape = 21,
    color = "black",
    stroke = 0.5
  ) +
  geom_label(
    aes(label = sprintf("%.1f", elpd_diff)),
    hjust         = -0.3,
    size          = 2.5,
    label.padding = unit(0.15, "lines"),
    label.size    = 0,
    fill          = "white",
    color         = "grey20"
  ) +
  coord_flip() +
  labs(
    x = NULL,
    y = expression(Delta * ELPD[LOO])
  ) +
  scale_fill_manual(
    values = c("TRUE" = "firebrick", "FALSE" = "grey70"),
    guide  = "none"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    plot.margin       = margin(5, 25, 5, 5),
    panel.grid.minor  = element_blank(),
    panel.grid.major.y = element_blank()
  )

loo_disclosure

ggsave(
  "figure_loo.png",
  loo_disclosure,
  width  = 6,
  height = 4,
  dpi    = 300
)
```

## LOO disclosure models (table)
```{r}
loo_output <- disclosurel_df  %>%
  select(Model, elpd_diff, se_diff)

loo_tabdisclose <- loo_output %>%
  knitr::kable(
    digits = 2,
    col.names = c("Model", "ΔELPD", "SE"),
    caption = "."
  ) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))

loo_tabdisclose
```
