---
title: Technology mediation in child sexual exploitation and abuse in Africa and Asia
authors: Ghai et al. 
subtitle: Modelling script (imputed analysis)
format: 
  typst:
    toc: true
    toc-depth: 2
  pdf:
    toc: true
    toc-depth: 2
    echo: false
    number_sections: true
    fig_caption: true
    fig_height: 12
    fig_width: 8
    latex_engine: xelatex
    fontsize: 10pt
    mainfont: "Times New Roman"
    header-includes:
      - \usepackage{pdflscape}   
      - \usepackage{geometry}     
      - \geometry{margin=1in}     
      - \usepackage{longtable} 
      - \usepackage{adjustbox}  
  html:
    toc: true
    toc-depth: 2
    self-contained: true
    number_sections: true
    fig_caption: true
    css: "assets/styles.css"
    highlight: "pygments"
---

## Analysis Set: Multiple Imputation
This script implements the full modelling pipeline with imputed data used to analyse predictors of disclosure of technology-facilitated CSEA. It includes all pre-registered confirmatory analyses, pre-registered exploratory models, and additional exploratory extensions, as well as diagnostics, multiple imputation, model comparisons, and figure generation. All models are estimated in a Bayesian framework using brms with survey weights and include all prespecified covariates.

**Model specifications**

(1) **Pre-registered confirmatory analysis**: Logistic regression with all prespecified predictors, survey weights, no random effects (imputed).

(2) **Pre-registered exploratory analysis**: Multilevel models with random intercepts by country (n = 12) for the three main disclosure outcomes (any, formal, informal) (imputed).

(3) **Exploratory (not pre-registered) main model**: Multilevel models with random intercepts and random slopes by country (imputed)

(4) **Pre-registered exploratory extension**: Random-effects models including an age × gender interaction, allowing  these effects to vary across countries (imputed).

(5) **Pre-registered exploratory robustness models**:  Regularised Bayesian logistic regression with horseshoe priors, fitted with random intercepts (and extended with random slopes) as sensitivity analyses (imputed).

```{r}
#| label: options
#| message: false
#| cache: false

# Load packages
library(gtsummary)
library(png)
library(tidyverse)
library(DataExplorer)
library(survey)
library(janitor)
library(grid)
library(gridExtra)
library(gridGraphics)
library(ggrepel)
library(mice)
library(brms)
library(scales)
library(dplyr)
library(purrr)
library(naniar)
library(collapse)
library(ggdist)
library(knitr)
library(rlang)
library(broom.mixed)
library(sjPlot)
library(RColorBrewer)
library(corrplot)
library(ggh4x)
library(bayesplot)
library(bayestestR)
library(patchwork)
library(rstan)
library(viridis)
library(marginaleffects)
library(kableExtra)
library(gt)
library(posterior)
library(tibble)
library(colorspace)
library(ggnewscale)
library(car)
library(performance)
library(srvyr)
library(tidybayes)

knitr::opts_chunk$set(dev = "png")

# Modelling: 
dir.create("models", FALSE)
options(
  brms.backend = "cmdstanr",
  mc.cores = min(parallel::detectCores(), 8),
  brms.threads = parallel::detectCores() %/% 4
)

# Make plots pretty 
theme_set(
  theme_linedraw() +
    theme(panel.grid = element_blank())
)

# Output options
opts_chunk$set(
  eval = TRUE,
  cache = TRUE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  echo = knitr::is_html_output()
)
options(digits = 2)

# Imputation and HMC iterations
# HMC iterations
ITER <- 2000
# Number of datasets to impute
M <- 30
```

```{r, echo=FALSE}
#| label: load-data-victim
d_victim <- readRDS("data-raw/victim_dh.rds")
```

```{r, echo=FALSE}
#| label: mutate-data-victim
#| include: false 
#| message: false
#| warning: false
#| cache: true
d_victim <- d_victim %>%
  select(
    pid = CBU_ID,
    sex,
    age,
    presex,
    nindex,
    parentmediate,
    sexed,
    urbanrural,
    helpseeking,
    digitalskills,
    COUNTRY,
    wgt_scaled,
    victim,
    starts_with("toldnoone_"),
    starts_with("abuse_"),
    starts_with("police_"),
    starts_with("helpline_"),
    starts_with("teacher_"),
    starts_with("sworker_"),
    starts_with("friend_"),
    starts_with("sibling_"),
    starts_with("father_"),
    starts_with("mother_"),
    starts_with("other_"),
    starts_with("othera_"),
     starts_with("otheropen_"),
     starts_with("rdontknow_"),
     starts_with("rprefer_")
  )
```

```{r disclosure-wrangling}
#| include: false 
#| message: false
# Identical to function in 2a_disclosure.qmd
# Duplicated here so this script runs independently
disclosure_data <- function(data) {
  
  # filter victims only
  victims <- data %>% filter(victim == 1)
  
  # disclosure channel names
  channels <- c("toldnoone", "police", "helpline", "teacher", "sworker", 
                "friend", "sibling", "father", "mother", "other", "othera")
  
  # function to check if disclosed any abuse type to this channel
  check_channel <- function(prefix, data) {
    # abuse types are a-i
    cols <- paste0(prefix, "_", letters[1:9])
    rowSums(data[cols], na.rm = TRUE) > 0
  }
  
  # apply to each channel
  for (ch in channels) {
    victims[[ch]] <- check_channel(ch, victims)
  }
  
  ## create disclosure categories
  victims %>%
    mutate(
      # any disclosure?
      toldall = police | helpline | teacher | sworker | friend | 
                 sibling | father | mother | other | othera,
      # formal vs informal
      toldformal = police | helpline | teacher | sworker,
      toldinformal = friend | sibling | father | mother | other | othera,
      
      # make mutually exclusive 
      no_disclosure = !toldall,
      informal_only = toldinformal & !toldformal,
      formal_only = toldformal & !toldinformal,
      both_channels = toldinformal & toldformal,
      
      # now factor
      disclosure_type = case_when(
        both_channels ~ "Both",
        informal_only ~ "Informal only",
        formal_only ~ "Formal only",
        no_disclosure ~ "None"
      ),
      disclosure_type = factor(disclosure_type, 
                              levels = c("None", "Informal only", "Formal only", "Both"))
    )
}

d_report <- disclosure_data(d_victim)
```

Load victim data and define labels including variations (to be used throughout)
```{r define-labels}
#| label: define-labels
#| include: false 
#| message: false
#| warning: false
#| cache: true
# Facet labels for predictors 
facet_labels <- c(
  "b_Intercept" = "Intercept",
  "b_sex1" = "Girl (vs Boy)",
  "b_sexGirl" = "Girl (vs Boy)",
  "sex1" = "Girl (vs Boy)",
  "sexGirl" = "Girl (vs Boy)",
  "b_age" = "Age (per year)",
  "b_sex1:age" = "Age:Gender interaction",  
  "age" = "Age (per year)",
  "b_presex1" = "Premarital sex",
  "presex1" = "Premarital sex",
  "b_nindex" = "Inequitable gender attitudes",
  "nindex" = "Inequitable gender attitudes",
  "b_parentmediate" = "Enabling parental mediation",
  "parentmediate" = "Enabling parental mediation",
  "b_sexed1" = "Sex education",
  "sexed1" = "Sex education",
  "b_helpseeking1" = "Help-seeking",
  "helpseeking1" = "Help-seeking",
  "b_digitalskills" = "Digital skills to report",
  "digitalskills" = "Digital skills to report"
)

 
# Report names for disclosure outcomes
report_names <- c(
  "toldall" = "Any Disclosure",
  "toldformal" = "Formal Disclosure",
  "toldinformal" = "Informal Disclosure"
)

# Clean labels for correlation plots
clean_labels <- c(
  "sex1" = "Girl (vs Boy)",
  "sexGirl" = "Girl (vs Boy)",
  "age" = "Age (per year)",
  "presex1" = "Premarital sex",
  "nindex" = "Inequitable gender attitudes",
  "parentmediate" = "Enabling parental mediation",
  "sexed1" = "Sex education",
  "helpseeking1" = "Help-seeking",
  "digitalskills" = "Digital skills"
)

# Define all channels
channels <- c(
  "police", 
  "helpline", 
  "sworker", 
  "teacher",
  "mother", 
  "father", 
  "sibling", 
  "friend",
  "other", 
  "othera"
  )

# labels
channel_labels <- c(
  police   = "Police",
  helpline = "Helpline",
  sworker  = "Social Worker",
  teacher  = "Teacher",
  mother   = "Mother",
  father   = "Father",
  sibling  = "Sibling",
  friend   = "Friend",
  other    = "Other",
  othera   = "Other Adult"
)

# Predictor term names
predictor_map <- c(
  b_Intercept     = "Intercept",
  b_sex1          = "Girls (vs Boys)",
  b_age           = "Age (per year)",
  b_presex1       = "Premarital sex",
  b_nindex        = "Inequitable attitudes towards sex",
  b_parentmediate = "Enabling parental mediation",
  b_sexed1        = "Sex education",
  b_helpseeking1  = "Help-seeking",
  b_digitalskills = "Digital skills to report"
)
predictors_to_keep <- names(predictor_map)
```

```{r}
#| include: false 
#| message: false
#| warning: false
#| cache: true
# Note: this version of summarise_draws_pop takes a named list of models
# and is specific to this script. The complete case script (3a) uses a 
# different single-model version of the same function.
summarise_draws_pop <- function(model_list, facet_labels, report_names) {
  names_list <- names(model_list)
  
  model_list %>%
    purrr::map(~ brms::posterior_summary(.x, variable = "^b_", regex = TRUE)) %>%
     purrr::map(as.data.frame) %>%
     purrr::map(~ tibble::rownames_to_column(.x, var = "term")) %>%
    bind_rows(.id = "report") %>%
    mutate(
      report = factor(report, levels = names_list, labels = report_names[names_list]),
      term = as.character(term)
    ) %>%
    filter(term != "b_Intercept") %>%
    mutate(
      predictor = case_when(
        term %in% names(facet_labels) ~ facet_labels[term],
        sub("^b_", "", term) %in% names(facet_labels) ~ facet_labels[sub("^b_", "", term)],
        TRUE ~ term
      ),
      Estimate = glue::glue(
        "{scales::number(Estimate, accuracy = 0.01)} ",
        "[{scales::number(Q2.5, accuracy = 0.01)}, ",
        "{scales::number(Q97.5, accuracy = 0.01)}]"
      )
    ) %>%
    select(predictor, report, Estimate) %>%
    pivot_wider(names_from = report, values_from = Estimate)
}

fmt_pct <- function(x, d=1) round(100*x, d)
safe_logical_counts <- function(x) {
  x <- as.logical(x)
  tab <- table(x, useNA="no")
  c(
    yes = if ("TRUE"  %in% names(tab)) as.integer(tab[["TRUE"]])  else 0L,
    no  = if ("FALSE" %in% names(tab)) as.integer(tab[["FALSE"]]) else 0L
  )
}
```

```{r, echo = FALSE}
#| include: false 
#| message: false
#| warning: false
#| cache: true

d_report <- disclosure_data(d_victim)

d_report <- d_report %>%
       select(
      c(
    -ends_with(c(
      "_a", 
      "_b", 
      "_c", 
      "_d", 
      "_e", 
      "_f", 
      "_g", 
      "_h", 
      "_i")),
      victim
    )
  )
```

# Missingness summary 
This section first produces a tidy missingness summary for key predictors, presenting counts and percentages. It then visualizes missing data across these variables with a vis_miss plot.
```{r}
#| label: tbl-missing
#| tbl-cap: Summary of missingness (only variables with missingness shown)
miss_summary <- miss_var_summary(d_report) %>% 
  filter(variable %in% c("sex", "age", "presex", "nindex", 
                         "parentmediate", "sexed", "helpseeking", 
                         "digitalskills")) %>%
  arrange(desc(pct_miss)) %>%
  mutate(
    n_miss = scales::comma(n_miss),
    pct_miss = sprintf("%.1f%%", pct_miss)
  ) %>%
  select(variable, n_miss, pct_miss)


miss_summary %>%
  kable(
    col.names = c("Variable", "N Missing", "% Missing"),
    align = c("l", "r", "r")
  ) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))
```

```{r}
#| label: fig-missing
#| fig-cap: Summary of missingness
#| fig-height: 4.4
miss_plot <- d_report %>% 
  select(presex, nindex, parentmediate, sexed, helpseeking, digitalskills) %>% 
  rename(
    "Premarital sex" = presex,
    "Inequitable gender attitudes" = nindex,  
    "Enabling parental mediation" = parentmediate,
    "Sex education" = sexed,
    "Help-seeking" = helpseeking,
    "Digital skills to report" = digitalskills
  ) %>%
  naniar::vis_miss(sort_miss = TRUE) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 16)) +
  coord_cartesian(clip = "off") +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(t = 5, r = 30, b = 10, l = 10)
  ) +
  labs(x = NULL, y = "Observations")

miss_plot
ggsave(
  "supplement_missingness.pdf",
  miss_plot,
  width = 6,
  height = 4,
  dpi = 300
)
```
## Impact of listwise deletion
Next, the code quantifies the impact of listwise deletion by defining a helper that flags complete cases for each outcome and calculates both raw and weighted losses using wgt_scaled. It applies this to the three outcomes (toldall, toldformal, toldinformal), then aggregates the results to report the minimum and maximum retained N and percentage loss. 
```{r}
predictor_vars <- c("sex", "age", "presex", "nindex", "parentmediate", 
                    "sexed", "helpseeking", "digitalskills")

# function to calculate complete cases (raw and weighted)
calc_complete <- function(data, outcome_var) {
  model_vars <- c(predictor_vars, outcome_var)
  
  data_complete <- data %>%
    mutate(complete = complete.cases(select(., all_of(model_vars))))
  
  # raw
  n_original <- nrow(data)
  n_complete <- sum(data_complete$complete)
  pct_lost <- (n_original - n_complete) / n_original * 100
  
  # weighted
  weighted_n_original <- sum(data$wgt_scaled, na.rm = TRUE)
  weighted_n_complete <- sum(data_complete$wgt_scaled[data_complete$complete], na.rm = TRUE)
  weighted_pct_lost <- (weighted_n_original - weighted_n_complete) / weighted_n_original * 100
  
  data.frame(
    outcome = outcome_var,
    n_original = n_original,
    n_complete = n_complete,
    n_lost = n_original - n_complete,
    pct_lost = pct_lost,
    weighted_n_original = round(weighted_n_original),
    weighted_n_complete = round(weighted_n_complete),
    weighted_n_lost = round(weighted_n_original - weighted_n_complete),
    weighted_pct_lost = weighted_pct_lost
  )
}

# calculate for all our outcomes
outcomes <- c("toldall", "toldformal", "toldinformal")
missing_df <- bind_rows(lapply(outcomes, function(x) calc_complete(d_report, x)))

# summary ranges
missing <- list(
  n_original = unique(missing_df$n_original),
  n_complete_min = min(missing_df$n_complete),
  n_complete_max = max(missing_df$n_complete),
  pct_lost_min = min(missing_df$pct_lost),
  pct_lost_max = max(missing_df$pct_lost),
  weighted_n_original = unique(missing_df$weighted_n_original),
  weighted_n_complete_min = min(missing_df$weighted_n_complete),
  weighted_n_complete_max = max(missing_df$weighted_n_complete),
  weighted_pct_lost_min = min(missing_df$weighted_pct_lost),
  weighted_pct_lost_max = max(missing_df$weighted_pct_lost)
)
```
Listwise deletion would have substantially reduced sample sizes across our analyses. For example, in the victim subset analysis examining age-sex interactions, listwise deletion would have reduced the sample from N=2,067 to N=1,149, 44% loss, or N = 2025 to 1105; 45% in weighted terms, substantially reducing statistical power.
```{r}
missing  <- tibble::tibble(
  Metric = c(
    "Original N",
    "Complete N (min–max)",
    "% lost (min–max)",
    "Weighted N (original)",
    "Weighted complete N (min–max)",
    "Weighted % lost (min–max)"
  ),
  Value = c(
    comma(missing$n_original),
    paste0(comma(missing$n_complete_min), "–", comma(missing$n_complete_max)),
    sprintf("%.1f–%.1f%%", missing$pct_lost_min, missing$pct_lost_max),
    comma(missing$weighted_n_original),
    paste0(comma(missing$weighted_n_complete_min), "–", comma(missing$weighted_n_complete_max)),
    sprintf("%.1f–%.1f%%", missing$weighted_pct_lost_min, missing$weighted_pct_lost_max)
  )
)

missing  %>%
  kable(align = c("l","r"), caption = "Sample loss under listwise deletion (raw and weighted).") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))
```

# Multiple Imputation

We used multiple imputation (M=30 datasets) by chained equations (MICE) with imputed datasets to address missingness under a Missing At Random (MAR) assumption. We fit all models with brm_multiple() so that each imputed dataset was analyzed separately and estimates were pooled across imputations using Rubin’s rules, thus propagating imputation uncertainty. Models included multilevel structure across 12 countries with different specifications (including random intercepts, slopes, interaction and penalised regressions). We use the mice package to generate M multiply imputed datasets. We exclude identifiers, weights, and outcome variables (toldall, toldformal, toldinformal) from being imputed.
```{r}
# exclude some variables from imputation
predictorMatrix <- make.predictorMatrix(d_report)
predictorMatrix[
  , 
  c("pid", "wgt_scaled", "toldall", "toldformal", "toldinformal")
] <- 0

path <- normalizePath("models/mice-report-intdata.rds", mustWork = FALSE)
if (!file.exists(path)) {
  d_report_mice <- mice(
    d_report, 
    m = M, 
    predictorMatrix = predictorMatrix, 
    print = FALSE
  )
  saveRDS(d_report_mice, path)
}
d_report_mice <- readRDS(path)
```


# Disclosure Analysis: Multiple imputations

## (1) Pre-Registered Confirmatory Analysis: Logistic Regression Model
First, we fit the confirmatory logistic regression which now incorporates multiple imputation. 
```{r}
#| output: false
fit_report_all_mice_glm <- brm_multiple(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + 
    digitalskills,
  data = d_report_mice,
  family = bernoulli(),
  iter = ITER,
  control = list(adapt_delta = 0.99),
  file = "models/brm-report-all-mice-glm"
)
```
We then summarise the posterior draws and present credible intervals
```{r, echo =FALSE}
#| label: tbl-report-mice-glm
#| tbl-cap: Results of GLM disclosure model (MI)

posterior_glm <- posterior_summary(fit_report_all_mice_glm)
posterior_df_mice <- as.data.frame(posterior_glm)

posterior_df_mice <- posterior_df_mice %>%
  tibble::rownames_to_column(var = "Parameter") %>%
  mutate(
    predictor = dplyr::recode(Parameter, !!!facet_labels, .default = Parameter),  # map labels
    `Odds Ratio` = exp(Estimate),
    `Lower OR CI` = exp(`Q2.5`),
    `Upper OR CI` = exp(`Q97.5`)
  ) %>%
  select(predictor, Estimate, `Q2.5`, `Q97.5`, `Odds Ratio`, `Lower OR CI`, `Upper OR CI`) %>%
  dplyr::rename(
    `Parameter` = predictor,
    `Lower CI` = `Q2.5`,
    `Upper CI` = `Q97.5`
  ) %>%
  knitr::kable(
    digits = 3,
     format.args = list(scientific = FALSE),
    col.names = c("Parameter", "Estimate", "Lower CI", "Upper CI", "Odds Ratio", "Lower OR CI", "Upper OR CI")
  )
posterior_df_mice 
```
## (2) Pre-registered Exploratory Analysis: Random Intercepts Model 

Second, we fit a multilevel logistic regression model that accounts for the hierarchical structure of the data, where children are nested within countries. By including random intercepts for country, the model adjusts for baseline differences in disclosure rates across the 12 countries. This analysis examines whether the relationship between key independent variables and disclosure varies according to the type of disclosure channel specifically, formal sources versus informal sources. This set of models was pre-registered as exploratory, allowing us to examine country level variation in predictors of disclosure.
```{r}
#| output: false
# all disclosure
fit_report_all_mice <- brm_multiple(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + digitalskills + 
    (1 | COUNTRY),
  data = d_report_mice,  
  family = bernoulli(),
  iter = ITER,
  control = list(adapt_delta = 0.99),
  file = "models/brm-disclosure-all-mice"
)

# formal disclosure
fit_report_formal_mice <- brm_multiple(
  toldformal | weights(wgt_scaled) ~ 
    sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + digitalskills + 
    (1 | COUNTRY),
  data = d_report_mice,  
  family = bernoulli(),
  iter = ITER,
  control = list(adapt_delta = 0.99),
  file = "models/brm-disclosure-formal-mice"
)

# informal disclosure
fit_report_informal_mice <- brm_multiple(
  toldinformal | weights(wgt_scaled) ~ 
    sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + digitalskills + 
    (1 | COUNTRY),
  data = d_report_mice,  
  family = bernoulli(),
  iter = ITER,
  control = list(adapt_delta = 0.99),
  file = "models/brm-disclosure-informal-mice"
)
```
This summary provides a side-by-side comparison of how each predictor varies across different disclosure contexts
```{r}
#| tbl-cap: Results of disclosure model with country as random effects (imputed models)

mice_models <- list(
  toldall =   fit_report_all_mice,
  toldformal = fit_report_formal_mice,
  toldinformal = fit_report_informal_mice
) 

summarise_draws_pop(mice_models, facet_labels, report_names) %>%
  kable(booktabs = TRUE, align = c("l", rep("r", 3))) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
```

\newpage

## (3) Exploratory Analysis (Not Pre-Registered): Random Intercepts and Slopes Model (Main Reported Analysis)

Third, we fit the primary model reported in the manuscript section Demographic and Socio-Cultural Factors Associated with Disclosure. This model extends the previous random intercepts model by including both random intercepts and random slopes for all predictors, allowing their effects to vary across countries. This more flexible specification captures cross-country differences not only in baseline disclosure rates but also in how demographic and sociocultural factors relate to disclosure. Although this was not pre-registered, the model builds directly on the previous model structure to provide a more context-sensitive interpretation of disclosure.
```{r}
#| output: false
# all disclosure
fit_report_all_mice_random <- brm_multiple(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + digitalskills + 
    (1 + sex + age + presex + nindex + 
       parentmediate + sexed + helpseeking + digitalskills | COUNTRY),
  data = d_report_mice,  
  family = bernoulli(),
  control = list(adapt_delta = 0.99),
  iter = ITER,
  file = "models/brm-disclosure-all-mice-random"
)

# formal disclosure
fit_report_formal_mice_random <- brm_multiple(
  toldformal | weights(wgt_scaled) ~ 
    sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + digitalskills + 
    (1 + sex + age + presex + nindex + 
       parentmediate + sexed + helpseeking + digitalskills | COUNTRY),
  data = d_report_mice,  
  family = bernoulli(),
  control = list(adapt_delta = 0.99),
  iter = ITER,
  file = "models/brm-disclosure-formal-mice-random"
)
# informal disclosure
fit_report_informal_mice_random <- brm_multiple(
  toldinformal | weights(wgt_scaled) ~ 
    sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + digitalskills + 
    (1 + sex + age + presex + nindex + 
       parentmediate + sexed + helpseeking + digitalskills | COUNTRY),
  data = d_report_mice,  
  family = bernoulli(),
  control = list(adapt_delta = 0.99),
  iter = ITER,
  file = "models/brm-disclosure-informal-mice-random"
)
```

We present summary of the Random Intercepts and Slopes Model below
```{r}
#| label: tbl-report-randomeffects
#| tbl-cap: Results of disclosure model with country as random effects and slopes (reported in manuscript)

miceslopes_models <- list(
  toldall =     fit_report_all_mice_random,
  toldformal =  fit_report_formal_mice_random,
  toldinformal =   fit_report_informal_mice_random
) 

summarise_draws_pop(miceslopes_models, facet_labels, report_names) %>%
  kable(booktabs = TRUE, align = c("l", rep("r", 3))) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
```

## Correlations Among Predictors in the Exploratory Model
Next we plot the posterior correlations among fixed-effect parameters in the random intercepts and slopes models. This plots correlations separately for all disclosures, formal disclosures, and informal disclosures. Correlations are derived from the posterior variance-covariance matrix of the fitted model.

```{r}
#| label: correlationsmatrix
#| fig-width: 11
#| fig-height: 8
#| fig-cap: "Correlation matrices of fixed-effect parameters from Bayesian logistic regression models with random intercepts and random slopes by country."

# parameter correlation matrix from model
plot_corrmatrix <- function(model, title, clean_labels = NULL,
                            show_intercept = FALSE,
                            number.digits = 2,
                            number.cex = 1.05,
                            tl.cex = 0.95) {
  # variance-covariance for fixed effects
  V <- vcov(model)
  M <- cov2cor(V)
  if (!show_intercept) {
    keep <- setdiff(colnames(M), "(Intercept)")
    M <- M[keep, keep, drop = FALSE]
  }
  if (!is.null(clean_labels)) {
    lbl <- colnames(M)
    pretty <- ifelse(lbl %in% names(clean_labels),
                     unname(clean_labels[lbl]),
                     lbl)
    colnames(M) <- rownames(M) <- pretty
  }

  # plot
  op <- par(oma = c(0, 0, 2.2, 0), mar = c(1.2, 1.2, 1.2, 1.2))
  on.exit(par(op), add = TRUE)

  corrplot::corrplot(
    M,
    method        = "number",
    type          = "upper",
    number.cex    = number.cex,
    number.digits = number.digits,
    tl.cex        = tl.cex,
    tl.srt        = 45,
    col           = colorRampPalette(c("darkblue", "white", "darkred"))(200),
    cl.cex        = 0.85,
    addgrid.col   = "gray85",
    diag          = FALSE,
    outline       = TRUE
  )
  mtext(title, outer = TRUE, cex = 1.15, line = 0.8)
  invisible(M)
}



# plot the correlation matrices 
plot_corrmatrix(fit_report_all_mice_random, "All", clean_labels = clean_labels)
plot_corrmatrix(fit_report_formal_mice_random, "Formal", clean_labels = clean_labels)
plot_corrmatrix(fit_report_informal_mice_random, "InFormal", clean_labels = clean_labels)
```


\newpage

## Leave-One-Out Cross-Validation
Next we evaluate LOO cross-validation: the model with random intercepts alone shows slightly better out-of-sample predictive performance than the model with random slopes. However, we note the difference is small.
```{r}
#| label: tbl-report-loo
#| tbl-cap: Model comparison 
path <- "models/loos.rds"
if (!file.exists(path)) {
  loos <- loo(
    fit_report_all_mice,
    fit_report_all_mice_random,
    compare = TRUE,
    model_names = c("Intercepts", "Intercepts & Slopes")
  )
  saveRDS(loos, path)
}
loos <- readRDS(path)
loos
```

\newpage
## (4) Pre-registered Exploratory Analysis: Random Intercepts, Slopes and Age-Gender Interactions

Fourth, we further extend the model by introducing random intercepts and random slopes for the country variable, while also including the interaction between age and gender. The addition of random slopes in this analysis goes beyond our exploratory pre-registered model, which only specified random effects and interactions. 

```{r}
#| output: true
fit_report_all_mice_random_interaction <- brm_multiple(
  toldall | weights(wgt_scaled) ~ 
    sex * age + presex + nindex + 
    parentmediate + sexed + helpseeking + digitalskills + 
    (1 + sex * age + presex + nindex + 
       parentmediate + sexed + helpseeking + digitalskills | COUNTRY),
  data = d_report_mice,  
  family = bernoulli(),
  control = list(adapt_delta = 0.99),
  iter = ITER,
  file = "models/brm-disclosure-all-mice-random-interaction"
)
```

```{r}
#| label: summary-function2
#| include: false 
#| message: false
#| warning: false
#| cache: true
summarise_draws_model <- function(model_list,
                                  label_map,
                                  show_or    = FALSE,
                                  term_regex = "^b_",
                                  col_labels = NULL) {
  if (is.null(names(model_list)) || any(names(model_list) == "")) {
    names(model_list) <- paste0("Model ", seq_along(model_list))
  }
  if (is.null(col_labels)) col_labels <- names(model_list)
  stopifnot(length(col_labels) == length(model_list))
  df <- model_list %>%
    map(~ brms::posterior_summary(.x, variable = term_regex, regex = TRUE) |> as.data.frame()) %>%
    map(tibble::rownames_to_column, var = "term") %>%
    bind_rows(.id = "model")
  current_ids <- unique(df$model)
  id_to_label <- stats::setNames(col_labels, current_ids)  

  df %>%
    mutate(
      model = dplyr::recode(model, !!!id_to_label),
      term2 = sub("^b_", "", .data[["term"]])
    ) %>%
    filter(.data[["term"]] != "b_Intercept") %>%
    dplyr::mutate(
      pred = dplyr::coalesce(unname(label_map[.data[["term"]]]),
                             unname(label_map[.data[["term2"]]]),
                             .data[["term2"]]),
      val = if (show_or) {
        glue::glue(
          "{scales::number(exp(.data[['Estimate']]), 0.01)} ",
          "[{scales::number(exp(.data[['Q2.5']]), 0.01)}, ",
          "{scales::number(exp(.data[['Q97.5']]), 0.01)}]"
        )
      } else {
        glue::glue(
          "{scales::number(.data[['Estimate']], 0.01)} ",
          "[{scales::number(.data[['Q2.5']], 0.01)}, ",
          "{scales::number(.data[['Q97.5']], 0.01)}]"
        )
      }
    ) %>%
    dplyr::select(predictor = pred, model, val) %>%
    tidyr::pivot_wider(names_from = model, values_from = val)
}
```
We show summaries below and also plot the associations 
```{r}
#| label: tbl-report-int
#| tbl-cap: Results of Interaction model

summarise_draws_model(
  list("Random slopes + interaction" = fit_report_all_mice_random_interaction),
  facet_labels
) %>% knitr::kable()
```

```{r}
#| label: fig-reportcountry
#| fig-cap: Association between age and probablity of technology-facilitated CSEA reporting/disclosing for boys and girls and each country.
# function to extract brms_conditional_effects
ce_ggplot <- function(brms_conditional_effects) {
  brms_conditional_effects %>%
    plot(plot = FALSE) %>%
    .[[1]]
}

# extract conditional effects
p_report_pop <- conditional_effects(
  fit_report_all_mice_random_interaction,
  effects = "age:sex",
  conditions = distinct(d_report, COUNTRY),
  re_formula = NULL,
  resolution = 9,
) %>% ce_ggplot()

p_report_pop <- p_report_pop +
  scale_color_brewer(
    palette = "Set1",
    aesthetics = c("color", "fill")
  ) +
   facet_wrap(~COUNTRY) +
  scale_y_continuous(
    "Probability of Disclosure"
  ) +
  scale_x_continuous(
    "Age (years)",
    labels = ~ . + 15
  ) +
  theme(
    legend.title = element_blank()
  )

# hack to order panels by average level of reporting
p_report_pop$data <- p_report_pop$data %>%
  mutate(COUNTRY = fct_reorder(COUNTRY, estimate__))

# plot with updated data
p_report_pop
```
We extract predicted probabilities of disclosure of technology-facilitated CSEA and how it varies by girls and boys
```{r}
#| label: extracted-probabilitiesdisclosure
#| tbl-cap: Predicted probabilities of disclosure of technology-facilitated CSEA

# First we extract the datalayer
report_prob <- ggplot_build(p_report_pop)$plot$data

# Adjust for age
report_prob$adjusted_age <- report_prob$effect1__ + 15

report_prob <- report_prob %>%
  mutate(
    adjusted_age = round(adjusted_age),
    sex = factor(sex, labels = c("Boy", "Girl"))
  )
# Filter and select adjusted values
extracted_prob_r <- report_prob %>%
  filter(
    adjusted_age %in% c(12, 17), sex %in% c("Boy", "Girl")
  ) %>%
  select(
    COUNTRY, adjusted_age, sex, estimate__, lower__, upper__
  )
# Predicted probabilities table
extracted_prob_r  %>%
  kable(col.names = c("Country", "Age", "Sex", "Estimate", "Lower Bound", "Upper Bound")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

## (5) Pre-registered Exploratory Analysis: Regularised Horseshoe Regression 

Finally, we run two regularised horseshoe regressions models. In the original pre-registration, we planned to regularize the model to prevent overfitting and ensure stability, as suggested by Gelman et al. (2020). Specifically, we intended to use LASSO regression, which introduces a penalty term to shrink coefficients toward zero. The penalty term's strength (lambda value) was to be determined using Bayesian methods, controlling the weighting of the penalty. Due to limitations with the software package brms, which made LASSO defunct, we opted for an alternative approach. Instead of LASSO, we applied the horseshoe prior as a conservative check. 
```{r}
#| label: fit-horseshoe-randomeffects
#| output: false
# set a horseshoe prior on the regression coefficients 
# scale_global = 0.5 sets the global shrinkage scale (controls overall regularisation)
prior <- prior(horseshoe(3, scale_global = 0.5), class = "b")

fit_report_mice_horseshoe <- brm_multiple(
  formula = toldall | weights(wgt_scaled) ~
    sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + digitalskills +
    (1 | COUNTRY),
  data = d_report_mice,
  family = bernoulli(),
  control = list(adapt_delta = 0.99),
  iter = ITER,
  prior = prior,
  file = "models/brm-report-horseshoe-random"
)
```

```{r}
#| label:  fit-horseshoe-randomeslopes
#| output: false
fit_report_mice_horseshoe_slope <- brm_multiple(
  formula = toldall | weights(wgt_scaled) ~
    sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + digitalskills +
    (1 + sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + digitalskills | COUNTRY),
  data = d_report_mice,
  family = bernoulli(),
  control = list(adapt_delta = 0.99),
  iter = ITER,
  prior = prior,
  file = "models/brm-report-horseshoe-random-slope"
)
```

```{r}
#| label: tbl-report-pen
#| tbl-cap: Results of penalised models

summarise_draws_model(
  list(
    fit_report_mice_horseshoe,
    fit_report_mice_horseshoe_slope
  ),
  facet_labels,
  col_labels = c("Random Intercepts + Regularised",
                 "Random Slopes + Regularised")
) %>% knitr::kable()

```

## Posterior Probability of Direction 
We further compute the posterior probability of direction (PD) and posterior means for each predictor across two sets of models examining disclosure of technology-facilitated child sexual exploitation and abuse (CSEA). A) Random Intercepts and Slopes Model (Main Reported Analysis) B) Regularlised regression models. PD values represent the degree of certainty in the direction of each estimated effect indicating the proportion of the posterior distribution that lies on the same side of zero (expressed as percentages)
```{r}
#| label: tbl-report-prb0
#| tbl-cap: Posterior probabilities of direction for each predictor across the All, Formal, and Informal disclosure models (Random intercepts and slopes).

pd <- function(model_list, predictors, labels) {
  model_list %>%
    purrr::map(~ as_draws_df(.x)) %>%
    purrr::map(~ {
      draws <- .x[, predictors, drop = FALSE]
      means <- colMeans(draws)
      pd <- sapply(draws, function(x) max(mean(x > 0), mean(x < 0)))
      direction <- ifelse(colMeans(draws) > 0, "positive", "negative")
      tibble::tibble(
        Predictor = predictors,
        Mean = round(means, 3),
        PD = scales::percent(pd, accuracy = 0.01, scale = 100),
        Direction = direction
      )
    }) %>%
    purrr::imap_dfr(~ dplyr::mutate(.x, Model = .y), .id = NULL) %>%
    dplyr::mutate(Predictor = labels[Predictor]) %>%
    dplyr::select(Model, Predictor, Mean, PD, Direction)
}


models1 <- list(
  All = fit_report_all_mice_random,
  Formal =  fit_report_formal_mice_random,
  Informal =  fit_report_informal_mice_random
)

predictors <- c(
  "b_sex1",
  "b_age",
  "b_presex1",
  "b_nindex",
  "b_parentmediate",
  "b_sexed1",
  "b_helpseeking1",
  "b_digitalskills"
)

pd(models1, predictors, facet_labels) %>% 
  kable() 
```
\newpage
```{r}
#| label: tbl-report-pb
#| tbl-cap: Posterior probabilities of direction for each predictor across the regularised regression models (intercept only and intercept and slopes combined)

models2 <- list(
  Intercepts = fit_report_mice_horseshoe,
  Slopes = fit_report_mice_horseshoe_slope
)

pd(models2, predictors, facet_labels) %>% 
  kable() 
```
# Modelling Figures
Finally, we plot all mansucript figures below.

### Halfeye Plots (Figure 4)
```{r}
#| label: Halfeye plots
#| fig-cap: Halfeye plots combining densities & intervals 
#| fig-width: 11
#| fig-height: 8

# posterior draws for all models
draws_df <- list(
  fit_report_all_mice_random,
  fit_report_formal_mice_random,
  fit_report_informal_mice_random
) %>%
  purrr::map(~ as_draws_df(.x, variable = "b_", regex = TRUE)) %>%
  bind_rows(.id = "model") %>%
  mutate(model = factor(model, levels = 1:3, labels = c("Any", "Formal", "Informal"))) %>%
  select(-starts_with("."), -b_Intercept) %>%
  pivot_longer(-model, names_to = "parameter", values_to = "value") %>%
  filter(parameter %in% names(facet_labels)) %>%
  mutate(name = facet_labels[parameter])

# compute credible intervals
intervals <- draws_df %>%
  group_by(name, model) %>%
  summarise(
    .lower = quantile(value, 0.025),
    .upper = quantile(value, 0.975),
    significant = (.lower > 0 | .upper < 0),
    credible_intervals = ifelse(significant, "95% CrI excludes 0", "95% CrI Includes 0"),
    .groups = "drop"
  )

# join summaries back into full posterior draws
draws_df <- left_join(draws_df, intervals, by = c("name", "model")) %>%
  mutate(
    name = forcats::fct_reorder(name, value, .fun = median, .desc = TRUE)
  )

# plot halfeye plot
halfeye_plot <- ggplot(draws_df, aes(
  x = value,
  y = name,
  fill = model,
  color = model,
  group = model
)) +
  stat_halfeye(
  aes(
    shape = as.character(credible_intervals)
  ),
  .width = c(0.66, 0.95),
  adjust = 0.6,
  slab_alpha = 0.4,
  interval_alpha = 1,
  point_alpha = 1,
  interval_size = 1.2,
  point_size = 2.5,
  position = position_dodge(width = 0.6)
  ) +
 scale_shape_manual(
  values = c("95% CrI excludes 0" = 17, "95% CrI Includes 0" = 16),
  name = ""
  ) +
  geom_vline(xintercept = 0, linetype = "dotted", color = "grey60") +
  scale_color_viridis_d(
    name = "Disclosure Channel",
    aesthetics = c("color", "fill"),  
    option = "inferno",
    begin = 0.3,
    end = 0.9,
    direction = -1
  ) +
  coord_cartesian(xlim = c(-1, 1)) +
  labs(
    title = "",
    x = "Parameter Estimate",
    y = "",
    fill = "Disclosure Channel",
    color = "Disclosure Channel"
  ) +
 theme_minimal(base_size = 10, base_family = "sans") +
  theme(
    axis.text.y  = element_text(family = "sans", size = 8, face = "bold"),
    axis.text.x  = element_text(family = "sans", size = 6),
    legend.title = element_text(family = "sans", size = 8, face = "bold"),
    legend.text  = element_text(family = "sans", size = 5),
    legend.position = "bottom",
    panel.grid   = element_blank(),
    plot.margin  = margin(10, 10, 10, 10)
  )
halfeye_plot

ggsave(
  "Figure4.pdf",
  halfeye_plot,
  width  = 18,
  height = 17,
  dpi    = 300,
  units  = "cm"
)
```

### Country-level Estimates 

We extract coefficients for all three models, then define function to process, label coefficients and combine them before plotting

```{r}
# country-level coefficients
coefs_all <- coef(fit_report_all_mice_random)$COUNTRY
coefs_formal <- coef(fit_report_formal_mice_random)$COUNTRY
coefs_informal <- coef(fit_report_informal_mice_random)$COUNTRY

# predictor labels
predictor_names <- c(
  "Intercept", "Girls (vs Boys)", "Age (per year)", "Premarital sex",
  "Inequitable gender attitudes", "Enabling parental mediation",
  "Sex education", "Help-seeking", "Digital skills to report"
)

# process coefficients
process_coefs <- function(coefs, report_type) {
  map_dfr(
    seq_len(dim(coefs)[[3]]),
    ~ as.data.frame(coefs[, , .x]) %>%
      rownames_to_column("country") %>%
      mutate(
        report = report_type,
        parameter = predictor_names[.x]
      )
  )
}

# combine
combined_coefs <- bind_rows(
  process_coefs(coefs_all, "All"),
  process_coefs(coefs_formal, "Formal"),
  process_coefs(coefs_informal, "Informal")
) %>%
  filter(parameter != "Intercept") %>%
  mutate(
    credible = ifelse(Q2.5 * Q97.5 > 0, "Excludes 0", "Includes 0"),
    sig = Q2.5 * Q97.5 > 0
  )
```

### Country-level estimates for any disclosure model (Figure 5)
```{r country-coefs-plot, warning=FALSE}
#| label: fig-country-coefs-clean
#| fig-cap: "Country-specific associations between predictors and disclosure. Points show posterior means; lines show 95% credible intervals. Solid elements indicate effects where 95% CI excludes zero; faded elements indicate non-credible effects."
#| fig-width: 14
#| fig-height: 10


# define regions
africa_order <- c("Ethiopia", "Kenya", "Mozambique", "Namibia", "Tanzania", "Uganda")
asia_order <- c("Cambodia", "Indonesia", "Malaysia", "Philippines", "Thailand", "Vietnam")

# prepare data
plot_coef <- combined_coefs %>%
  filter(report == "All") %>%
  mutate(
    region = case_when(
      country %in% africa_order ~ "Africa",
      country %in% asia_order   ~ "Asia",
      TRUE ~ NA_character_
    ),
    country = factor(country, levels = rev(c(africa_order, asia_order))),
    sig = Q2.5 * Q97.5 > 0
  ) %>%
  filter(!is.na(region))

# plot coef for any disclosure model
countrycoefs <- ggplot(plot_coef, aes(x = Estimate, y = country)) +
  geom_vline(xintercept = 0, linetype = "solid", linewidth = 0.3, color = "grey40") +
  geom_segment(
    data = ~ subset(.x, !sig),
    aes(x = Q2.5, xend = Q97.5, y = country, yend = country),
    color = "grey78", linewidth = 0.7
  ) +
  geom_point(
    data = ~ subset(.x, !sig),
    color = "grey70", size = 2.5, shape = 16
  ) +
  geom_segment(
    data = ~ subset(.x, sig),
    aes(x = Q2.5, xend = Q97.5, y = country, yend = country, color = region),
    linewidth = 1.2
  ) +
  geom_point(
    data = ~ subset(.x, sig),
    aes(color = region),
    size = 3.2, shape = 16
  ) +
  scale_color_manual(
    values = c("Africa" = "#3B0F70", "Asia" = "#E69F00"),
    name   = NULL
  ) +
  guides(color = guide_legend(override.aes = list(linewidth = 1.5, size = 3))) +
  facet_wrap(~ parameter, scales = "free_x", nrow = 2) +
  scale_y_discrete(expand = expansion(add = c(0.5, 0.5))) +
  labs(x = "Estimate (log-odds)", y = NULL) +
  theme_minimal(base_size = 10, base_family = "sans") +
  theme(
    strip.background = element_blank(),
    strip.text = element_text(color = "black", face = "bold", 
                              size = 7, family = "sans",
                              margin = margin(t = 3, b = 3)),
    panel.background = element_rect(fill = "white", colour = NA),
    plot.background  = element_rect(fill = "white", colour = NA),
    panel.border     = element_blank(),  
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y  = element_text(size = 9, face = "bold", family = "sans"),
    axis.text.x  = element_text(size = 8, family = "sans"),
    axis.title.x = element_text(size = 10, face = "bold", family = "sans",
                                margin = margin(t = 8)),
    axis.line    = element_line(color = "black", linewidth = 0.4),
    axis.ticks   = element_line(color = "black", linewidth = 0.4),
    axis.ticks.length = unit(3, "pt"),
    legend.position  = "bottom",
    legend.text      = element_text(size = 9, family = "sans"),
    legend.key.width = unit(1, "cm"),
    plot.margin      = margin(10, 10, 10, 10)
  )

countrycoefs

ggsave(
  "Figure5.pdf",
  countrycoefs,
  width  = 20,
  height = 17,
  dpi    = 300,
  units  = "cm"
)
```
### Country-level estimates for formal and informal disclosure model (Extended Data Fig 3)
```{r}
#| label: fig-formal-informal-combined
#| fig-cap: "Country-specific associations with disclosure by channel type. Points show posterior means for formal (orange) and informal (red) channels; horizontal lines show 95% credible intervals. Solid points indicate credible effects (95% CI excludes zero); faded points indicate non-credible effects. Dotted horizontal line separates African and Asian countries."
#| fig-width: 14
#| fig-height: 18

# country order 
countries <- c(
  "Ethiopia","Kenya","Mozambique","Namibia","Tanzania","Uganda",
  "Cambodia","Indonesia","Malaysia","Philippines","Thailand","Vietnam"
)

# prepare data
plot_formalinformal <- combined_coefs %>%
  dplyr::mutate(
    country = factor(country, levels = rev(countries)),   
    y_base  = as.numeric(country),
    y       = y_base + ifelse(report == "Formal",  +0.20,  -0.20) 
  )

# plot 
formalinformal_plot <- ggplot(plot_formalinformal, aes(x = Estimate, y = y)) +
  geom_vline(xintercept = 0, linetype = "solid", linewidth = 0.3, color = "grey30") +
  # Non-credible (grey)
  geom_linerange(
    data = ~ subset(.x, !sig),
    aes(xmin = Q2.5, xmax = Q97.5, linetype = report),
    linewidth = 0.6, color = "grey75", show.legend = FALSE
  ) +
  geom_point(
    data = ~ subset(.x, !sig),
    aes(shape = report),
    size = 2.2, color = "grey60", stroke = 0.3, show.legend = FALSE
  ) +
  # credible (colored)
  geom_linerange(
    data = ~ subset(.x, sig),
    aes(xmin = Q2.5, xmax = Q97.5, color = report, linetype = report),
    linewidth = 1.0
  ) +
  geom_point(
    data = ~ subset(.x, sig),
    aes(color = report, shape = report),
    size = 2.8
  ) +
  scale_color_manual(values = c("Formal" = "#3B0F70", "Informal" = "#E69F00"), name = NULL) +
  scale_shape_manual(values = c("Formal" = 16, "Informal" = 17), name = NULL) +
  scale_linetype_manual(values = c("Formal" = "solid", "Informal" = "solid"), name = NULL) +
  facet_wrap(~ parameter, scales = "free_x", nrow = 2) +
  labs(x = "Estimate (log-odds)", y = NULL) +
  scale_y_continuous(
  breaks = seq_along(rev(countries)),
  labels = rev(countries),
  expand = expansion(mult = c(0.02, 0.02))
  ) +
  theme_minimal(base_size = 10, base_family = "sans") +
  theme(
    panel.background = element_rect(fill = "white", color = NA),
    plot.background  = element_rect(fill = "white", color = NA),
    panel.border     = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text       = element_text(color = "black", face = "bold",
                                    size = 10, family = "sans",
                                    margin = margin(t = 3, b = 3)),
    axis.text.y      = element_text(size = 8, face = "bold", family = "sans"),
    axis.text.x      = element_text(size = 8, family = "sans"),
    axis.line        = element_line(color = "black", linewidth = 0.4),
    axis.ticks       = element_line(color = "black", linewidth = 0.4),
    axis.ticks.length = unit(3, "pt"),
    legend.position  = "bottom",
    legend.key       = element_blank(),
    legend.key.width = unit(1, "cm"),
    plot.margin      = margin(6, 6, 6, 6)
  )

formalinformal_plot

ggsave(
  "Extended Data Fig.3.tif", 
  formalinformal_plot,
  width = 12,
  height = 17,
  dpi = 600,
  compression = "lzw"  
)
```

### Credible Associations
We prepare coefficient data for summarising credible and directional effects
```{r}
combined_coefs2 <- combined_coefs %>%
  mutate(
    credible = if_else(Q2.5 * Q97.5 > 0, "Credible", "Not credible"),
    direction = if_else(Estimate > 0, "Positive", "Negative"),
    country = as.character(country)
  )

# comparing credible vs non-credible results 
# by parameter, disclosure and country
credible_coefs <- combined_coefs2 %>%
  group_by(
    parameter, report, country, credible, direction
  ) %>%
  summarise(n = n()) %>%
  group_by(
    parameter, report, country
  ) %>%
  mutate(percent = n / sum(n)) %>%
  mutate(
    x = interaction(credible, direction, sep = " & ")
  ) %>%
  select(
    -credible, -direction
  ) %>%
  pivot_wider(
    names_from = x,
    values_from = percent
  ) %>%
  mutate(
    across(everything(), ~ ifelse(is.na(.), 0, .))
  )
```

Now we print a table of credible associations
```{r}
# Country-specific posterior coefficients 
# PD computed under a normal approximation to the posterior
combined_coefs <- combined_coefs %>%
  mutate(
    PD_value     = if_else(
      Estimate > 0, 
      pnorm(Estimate / Est.Error), 
      1 - pnorm(Estimate / Est.Error)
    ),
    credible_interval = if_else(Q2.5 * Q97.5 > 0, "Yes", "No")
  )

coef_supplementary <- combined_coefs %>%
  mutate(
    across(c(Estimate, `Q2.5`, `Q97.5`), ~ round(.x, 3)),
    `PD` = scales::percent(PD_value, accuracy = 0.1)
  ) %>%
  select(
    Country       = country,
    Model         = report,
    Parameter     = parameter,
    Estimate,
    `Q2.5`,
    `Q97.5`,
    `PD`,
    `Excludes 0?` = credible_interval
  ) %>%
  arrange(Country, Model, Parameter)


coef_supplementary  %>%
  kable(
    booktabs = TRUE,
    caption  = "Country-specific posterior coefficients (log-odds) for disclosure models (All, Formal, Informal)."
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    font_size = 8
  ) %>%
  collapse_rows(columns = 1:2, valign = "top")
```

```{r}
#| label: modelsfrom 3a_disclosure_scriptfor-diagnostics
#| include: false 
#| message: false
#| warning: false
#| cache: true
#| output: false
fit_report_all_glm <- brm(
  toldall | weights(wgt_scaled) ~ 
    sex + age + presex + nindex + 
    parentmediate + sexed + helpseeking + 
    digitalskills,
  data = d_report,
  family = bernoulli(),
  control = list(adapt_delta = 0.99),
  file = "models/brm-report-all-glm"
)

fit_report_all <- brm(
  model_toldall,
  data = d_report,
  family = bernoulli(),
  silent = 0,
  file = "models/brm-report-all",
  iter = ITER,
  control = list(adapt_delta = 0.99)
)
```

```{r}
#| label: plabel
#| include: false 
#| message: false
#| warning: false
#| cache: true
predictor_names <- c(
  "b_sex1" = "Girl (vs Boy)",
  "b_age" =  "Age (per year)",
  "b_presex1" = "Premarital sex",
  "b_nindex" = "Inequitable gender attitudes",
  "b_parentmediate" = "Enabling parental mediation",
  "b_sexed1" = "Sex education",
  "b_helpseeking1" = "Help-seeking",
  "b_digitalskills" = "Digital skills to report"
)
```

### Model Comparisons (Extended Data Fig 4)
Finally, we show main results of those models for robustness checking
```{r}
#| label: fig-modelcomparisons
#| fig-cap: "Comparing all permutations of models"
#| fig-width: 17
#| fig-height: 10
#| fig-pos: "H"

# function again to summarise posterior draws 
summarise_draws_comp <- function(fit, variable = c("b_", "sd_", "cor_")) {
  fit %>%
    as_draws_df(variable = variable, regex = TRUE) %>%
    summarise_draws(
      mean, sd, ~ quantile2(.x, c(0.025, 0.975))
    )
}

# summary function to all the models
comparisons <- list(
  fit_report_all_glm,
  fit_report_all,
  fit_report_all_mice_glm,
  fit_report_all_mice,
  fit_report_all_mice_random,
  fit_report_mice_horseshoe,
  fit_report_mice_horseshoe_slope
) %>% 
  purrr::map(~ summarise_draws_comp(.x, variable = "^b_")) %>% 
  dplyr::bind_rows(.id = "model") %>%
  dplyr::filter(variable != "b_Intercept",
                variable %in% names(predictor_names)) %>%
  dplyr::mutate(
    model = factor(
      model,
      levels = 1:7,
      labels = c(
        "No Multiple Imputations + GLM",
        "No Multiple Imputations + Random Intercepts",
        "Multiple Imputations + GLM",
        "Multiple Imputations + Random Intercepts",
        "Multiple Imputations + Random Slopes",
        "Multiple Imputations + Random Intercepts + Regularised",
        "Multiple Imputations + Random Slopes + Regularised"
      )
    ),
    label = dplyr::recode(variable, !!!predictor_names),
    label = forcats::fct_reorder(label, mean),
    significant = (q2.5 > 0 | q97.5 < 0)
  )

# plot
comparison <- ggplot(comparisons, aes(mean, label, color = model, alpha = significant)) +
  geom_vline(xintercept = 0, linetype = "dotted", linewidth = 0.3, color = "grey50") +
  geom_pointinterval(
    aes(xmin = q2.5, xmax = q97.5),
    position = position_dodge(width = 0.6),
    fatten_point = 3,
    size = 1.3
  ) +
  scale_x_continuous("Estimate", breaks = extended_breaks(n = 7)) +
  scale_alpha_manual(
    name = "95% CrI excludes 0",
    values = c("TRUE" = 1, "FALSE" = 0.2)
  ) +
  scale_color_brewer(name = "Model", palette = "Dark2") +
  guides(color = guide_legend(reverse = TRUE)) +
  theme_minimal(base_family = "sans", base_size = 16) +
  theme(
    axis.title.y       = element_blank(),
    axis.text.y        = element_text(size = 18, face = "bold", family = "sans"),
    axis.text.x        = element_text(size = 13, family = "sans"),
    axis.title.x       = element_text(size = 18, face = "bold", family = "sans"),
    legend.title       = element_text(size = 18, face = "bold", family = "sans"),
    legend.text        = element_text(size = 15, family = "sans"),
    legend.key.size    = unit(1.4, "lines"),
    panel.border       = element_rect(color = "black", fill = NA, linewidth = 0.8),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "grey85"),
    plot.margin        = margin(20, 60, 20, 20)
  )

comparison 

ggsave(
  "Extended Data Fig.4.tif", 
  comparison,
  width = 16, 
  height = 15, 
  dpi = 300, 
  units = "in",
  compression = "lzw"  
)
```

\newpage
# Model Checking 

Because models were fit using multiply imputed datasets via brm_multiple, we took additional steps to ensure robust convergence diagnostics beyond default summaries. Standard diagnostics such as R̂ can be misleading when computed by pooling chains across imputations. This is because chains are technically independent across imputations and may exhibit good within-imputation mixing but poor convergence when aggregated—especially for parameters linked to variables with high missingness (e.g., the nindex).

To address this, we computed $\hat{R}$ separately for each set of chains corresponding to each of the M imputed datasets. For each parameter, we report the worst (i.e., highest)̂ $\hat{R}$  value observed across imputations. We also examined the presence of divergent transitions across imputed datasets to identify potential sampling issues in the posterior geometry. This conservative approach allows us to more effectively identify any convergence issues that might otherwise be masked by averaging. In addition to numerical convergence checks, we conducted graphical diagnostics for each model, including:

1. Trace plots for fixed and group-level effects (b_, sd_);
2. Histograms of $\hat{R}$ values across all parameters, to assess overall convergence distribution;
3. Posterior predictive checks, stratified by sex, to assess model fit to the observed data.

These visualisations are shown for each main model below.
```{r}
#| label: modelsfrom 2b_CSEAmodellingscript
#| include: false 
#| message: false
#| warning: false
#| cache: true
fit_victim <- brm(
  victim | weights(wgt_scaled) ~ sex * age + (sex * age | COUNTRY),
  data = d_victim,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  iter = ITER,
  file = "models/brm-victim"
)
fit_urban2 <- brm(
  victim | weights(wgt_scaled) ~ sex * age + urbanrural + (sex * age  | COUNTRY),
  data = d_victim,
  family = bernoulli(),
  silent = 0,
  backend = "cmdstanr",
  iter = ITER,
  file = "models/brm-urban2",
)
```

The following visualises the worst-case $\hat{R}$ values across each of the $M$ multiply imputed datasets, grouping chains by imputation.
```{r}
#| cache: false
#' Find worst Rhat for each parameter among M sets of K chains
#' This is useful for a brm_multiple model fitted to MICE data as it calculates
#' Rhat separately for each MI dataset.
#' @param model a brms model fit object (brm_multiple)
#' @param m Number of imputed datasets
#' @param k Number of chains per model (usually 4; the brm_multiple model will have m*k chains)


rhat_worst_hist <- function(model, m, k) {
  rhats <- as_draws_df(model, variable = c("b_", "sd_", "cor_"), regex = TRUE) %>% 
    mutate(chainset = ((.chain) - 1) %/% k) %>% 
    group_by(chainset) %>%
    group_modify(~ summarise_draws(.x, rhat)) %>% 
    ungroup() %>% 
    filter(rhat == max(abs(rhat)), .by = variable) %>%
    pull(rhat)
  
  bayesplot::mcmc_rhat_hist(rhats) +
    scale_x_continuous(labels = ~ number(.x, accuracy = 0.001)) +
    labs(x = "Rhat", y = "Frequency") +
    theme_minimal() +
    theme(
      axis.title = element_text(size = 10),
      axis.text  = element_text(size = 8)
    )
}
```
Set predictor names 
```{r}
predictor_names <- c(
  # fixed effects
  "b_Intercept"        = "Intercept",
  "b_sex1"             = "Girl (vs Boy)",
  "b_age"              = "Age (per year)",
  "b_presex1"          = "Premarital sex",
  "b_nindex"           = "Inequitable gender attitudes",
  "b_parentmediate"    = "Enabling parental mediation",
  "b_sexed1"           = "Sex education",
  "b_helpseeking1"     = "Help-seeking",
  "b_digitalskills"    = "Digital skills",
  "b_sex1:age"         = "Girl × Age interaction",
  "b_urbanruralRural"  = "Rural (vs Peri-urban)",
  "b_urbanruralUrban"  = "Urban (vs Peri-urban)",
  
  # random effects (SDs) 
  "sd_COUNTRY__Intercept" = "SD: Country Intercept",
  "sd_COUNTRY__sex1"      = "SD: Country × Gender",
  "sd_COUNTRY__age"       = "SD: Country × Age",
  "sd_COUNTRY__sex1:age"  = "SD: Country × (Gender × Age)",
   "sd_COUNTRY__presex1"       = "SD: Country × Premarital-sex",
  "sd_COUNTRY__nindex"        = "SD: Country × Gender attitudes",
  "sd_COUNTRY__parentmediate" = "SD: Country × Parental mediation",
  "sd_COUNTRY__sexed1"        = "SD: Country × Sex education",
  "sd_COUNTRY__helpseeking1"  = "SD: Country × Help-seeking",
  "sd_COUNTRY__digitalskills" = "SD: Country × Digital skills",
  
  # correlations 
  "cor_COUNTRY__Intercept__sex1"   = "Cor: Intercept–Sex",
  "cor_COUNTRY__Intercept__age"    = "Cor: Intercept–Age",
  "cor_COUNTRY__sex1__age"         = "Cor: Sex–Age"

)
```

```{r}
#| cache: false
checks <- function(model, m = M, k = 4, predictor_labels = predictor_names) {
  
  # labeller for facet strips
  param_labeller <- function(x) {
    ifelse(x %in% names(predictor_labels),
           predictor_labels[x],
           x)
  }
  
  # trace plots for fixed and random effects
  pa <- mcmc_plot(
    model,
    type    = "trace",
    variable = c("b_", "sd_"),
    regex   = TRUE,
    facet_args = list(
      labeller = ggplot2::labeller(parameter = param_labeller)
    )
  ) +
    labs(title = "A. Trace Plots", x = "Iteration", y = "Parameter") +
    theme_minimal() +
    theme(
      plot.title  = element_text(size = 10, face = "bold"),
      axis.title  = element_text(size = 10),
      axis.text   = element_text(size = 8),
      axis.text.y = element_text(hjust = 1)
    )
  
  # r-hat histogram 
  pb <- rhat_worst_hist(model, m, k) +
    labs(title = "B. R̂ Histogram") +
    theme(
      plot.title = element_text(size = 10, face = "bold")
    )
  
  # posterior predictive check by sex
  pc <- pp_check(
    model,
    type  = "bars_grouped",
    group = "sex"
  ) +
    labs(
      title = "C. Posterior Predictive",
      x = "Predicted", y = "Frequency"
    ) +
    scale_x_continuous(labels = ~ number(.x, accuracy = 0.001)) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 10, face = "bold"),
      axis.title = element_text(size = 10),
      axis.text  = element_text(size = 8)
    )
  
  # combine plots
  (pa / (pb | pc)) +
    plot_layout(heights = c(7, 3)) +
    plot_annotation(tag_levels = NULL) &
    theme(legend.position = "none")
}
```
\newpage
R-hat values slightly exceeded 1.01 for a few parameters across imputations. These deviations likely reflect expected variability across imputed datasets, rather than just convergence failures. 

To formalize this evaluation, we tabulate convergence summaries below. For each model, we report the worst R-hat across imputations and the total number of divergent transitions observed. E-BFMI is not available for models fit via multiple imputation (brm_multiple), as pooling across imputed datasets does not yield a single joint sampler trajectory
```{r, results='asis'}
#| label: tbl-indep
#| tbl-cap: "Model convergence diagnostics across multiply imputed datasets"

# energy extraction helper for E-BFMI
.get_energies <- function(fit) {
  if ("CmdStanMCMC" %in% class(fit)) {
    sd <- tryCatch(fit$sampler_diagnostics(), error = function(e) NULL)
    if (!is.null(sd) && "energy__" %in% names(sd)) return(as.numeric(sd$energy__))
  }
  if ("stanfit" %in% class(fit)) {
    sp <- tryCatch(rstan::get_sampler_params(fit, inc_warmup = FALSE), error = function(e) NULL)
    if (!is.null(sp)) return(as.numeric(unlist(lapply(sp, function(m) m[, "energy__"]))))
  }
  numeric(0)
}

get_ebfmi <- function(model) {
  E <- unlist(lapply(model$fits, .get_energies))
  if (length(E) < 10) return(NA_real_)
  var(diff(E)) / var(E)
}

get_divergences <- function(model) {
  total_divs <- 0
  for (fit in model$fits) {
    if ("CmdStanMCMC" %in% class(fit)) {
      diag <- tryCatch(fit$diagnostic_summary(), error = function(e) NULL)
      if (is.data.frame(diag) && "divergent__" %in% names(diag))
        total_divs <- total_divs + sum(diag$divergent__, na.rm = TRUE)
    } else if (!is.null(fit@sim$diagnostics)) {
      total_divs <- total_divs + tryCatch(
        sum(fit@sim$diagnostics[,, "divergent__"], na.rm = TRUE), error = function(e) 0
      )
    }
  }
  total_divs
}

get_treedepth_hits <- function(model, max_td = 10) {
  total <- 0L
  for (fit in model$fits) {
    if ("CmdStanMCMC" %in% class(fit)) {
      ds <- tryCatch(fit$diagnostic_summary(), error = function(e) NULL)
      if (is.data.frame(ds) && "max_depth__" %in% names(ds))
        total <- total + sum(ds$max_depth__ >= max_td, na.rm = TRUE)
    }
  }
  total
}

model_summary_convergence <- function(model, k = 4, model_name = "Model") {
  draws <- posterior::as_draws_df(model, variable = c("b_", "sd_", "cor_"), regex = TRUE) %>%
    mutate(chainset = (.chain - 1L) %/% k)

  diag <- draws %>%
    group_by(chainset) %>%
    group_modify(~ posterior::summarise_draws(.x, rhat, ess_bulk, ess_tail)) %>%
    ungroup()

  tibble(
    Model          = model_name,
    Worst_Rhat     = max(diag$rhat,     na.rm = TRUE),
    Min_ESS_bulk   = min(diag$ess_bulk, na.rm = TRUE),
    Min_ESS_tail   = min(diag$ess_tail, na.rm = TRUE),
    Divergences    = get_divergences(model),
    Treedepth_hits = get_treedepth_hits(model),
    E_BFMI         = round(get_ebfmi(model), 3)
  )
}

summary_table <- bind_rows(
  model_summary_convergence(fit_report_all_mice_random,      model_name = "Disclosure: All"),
  model_summary_convergence(fit_report_formal_mice_random,   model_name = "Disclosure: Formal"),
  model_summary_convergence(fit_report_informal_mice_random, model_name = "Disclosure: Informal"),
  model_summary_convergence(fit_report_mice_horseshoe,       model_name = "Disclosure: Horseshoe (RI)"),
  model_summary_convergence(fit_report_mice_horseshoe_slope, model_name = "Disclosure: Horseshoe (RS)")
)

summary_table %>%
  mutate(Worst_Rhat = sprintf("%.6f", Worst_Rhat)) %>%
  kable(
    col.names = c("Model", "Worst R̂", "Min ESS (bulk)", "Min ESS (tail)",
                  "Divergences", "Treedepth hits", "E-BFMI"),
    booktabs = TRUE, longtable = TRUE, escape = FALSE
  ) %>%
  kable_styling(latex_options = c("striped", "hold_position", "repeat_header", "scale_down"),
                font_size = 9) %>%
  column_spec(1, width = "6cm") %>%
  column_spec(2, width = "3cm") %>%
  row_spec(which(summary_table$Divergences > 0 | summary_table$Worst_Rhat >= 1.05), bold = TRUE)
```
\newpage
```{r}
#| label: fig-ppcheck-vic
#| cache: false
#| fig-height: 8.4
#| fig-width: 12
#| fig-cap: "Graphical diagnostics of the demographic model for technology-facilitated CSEA disclosure, including trace plots, R̂ histogram, and posterior predictive check."
checks(fit_victim)
```

```{r}
#| label: fig-ppcheck-urban
#| cache: false
#| fig-height: 8.4
#| fig-width: 12
#| fig-cap: "Graphical diagnostics of the urbanisation model for technology-facilitated CSEA disclosure, including trace plots, R̂ histogram, and posterior predictive check."
checks(fit_urban2)
```

```{r}
#| label: fig-ppcheck-report-1
#| cache: false
#| fig-height: 8.4
#| fig-width: 10
#| fig-cap: "Graphical diagnostics for the disclosure model with random intercepts and missingness model, including posterior predictive density."
checks(fit_report_all)
```
\newpage
```{r}
#| label: fig-ppcheck-int-mice-4
#| cache: false
#| fig-height: 8.4
#| fig-width: 10
#| fig-cap: "Graphical diagnostics for the disclosure model with random slopes and an age-by-sex interaction, including posterior predictive density."
checks(fit_report_all_mice_random_interaction, m = M, k = 4)
```

\newpage
```{r}
#| label: fig-ppcheck-report-eff
#| cache: false
#| fig-height: 8.4
#| fig-width: 12
#| fig-cap: "Graphical diagnostics for the disclosure model with random effects only, including posterior predictive density."
checks(fit_report_all_mice, m = M, k = 4)
```

```{r}
#| label: fig-ppcheck-report-eff2
#| cache: false
#| fig-height: 8.4
#| fig-width: 12
#| fig-cap: "Graphical diagnostics for the formal disclosure model with random effects only, including posterior predictive density."
checks(fit_report_formal_mice, m = M, k = 4)
```

\newpage
```{r}
#| label: fig-ppcheck-report-eff3
#| cache: false
#| fig-height: 8.4
#| fig-width: 12
#| fig-cap: "Graphical diagnostics for the informal disclosure model with random effects only, including posterior predictive density."
checks(fit_report_informal_mice, m = M, k = 4)
```

\newpage
```{r}
#| label: fig-ppcheck-report-mice-1
#| cache: false
#| fig-height: 8.4
#| fig-width: 12
#| fig-cap: "Graphical diagnostics for the disclosure model with random slopes, including posterior predictive density."
checks(fit_report_all_mice_random, m = M, k = 4)
```
\newpage
```{r}
#| label: fig-ppcheck-formal-mice-2
#| cache: false
#| fig-height: 8.4
#| fig-width: 12
#| fig-cap: "Graphical diagnostics for the formal disclosure model with random slopes, including posterior predictive density."
checks(fit_report_formal_mice_random, m = M, k = 4)
```
\newpage
```{r}
#| label: fig-ppcheck-informal-mice-3
#| cache: false
#| fig-height: 8.4
#| fig-width: 12
#| fig-cap: "Graphical diagnostics for the informal disclosure model with random slopes, including posterior predictive density."
checks(fit_report_informal_mice_random, m = M, k = 4)
```

```{r}
#| label: fig-ppcheck-horshoe
#| cache: false
#| fig-height: 8.4
#| fig-width: 12
#| fig-cap: "Graphical diagnostics for the horseshoe model with random slopes, including posterior predictive density."
checks(fit_report_mice_horseshoe, m = M, k = 4)

```

```{r}
#| label: fig-ppcheck-horshoeslope
#| cache: false
#| fig-height: 8.4
#| fig-width: 12
#| fig-cap: "Graphical diagnostics for the horseshoe model with random slopes, including posterior predictive density."
checks(fit_report_mice_horseshoe_slope, m = M, k = 4)

```
